---
title: "Exploratory analyses"
author: "Ashish"
date: "`r Sys.Date()`"
output: rmdformats::readthedown
---


# Initialization
```{r, message=FALSE}
library(lavaan)
library(lmerTest)
library(here)
library(tidyverse)
library(glue)
library(tidylog)
require(rmdformats)
theme_set(theme_bw())
```

# Preprocessing 

## Read data
```{r, message=F}

data_filepath <- "data/proc/national_study_2b_proc.csv"
df_file <- read_csv(here("data/proc/national_study_2b_proc.csv"))
df_proc <- df_file %>% 
  mutate(high_ace = as.factor(high_ace)) %>%   
  mutate(income = factor(income, levels = c(
    "Less than $10,000",
    "$10,000 to $19,999",
    "$20,000 to $29,999",
    "$30,000 to $39,999",
    "$40,000 to $49,999",
    "$50,000 to $59,999",
    "$60,000 to $69,999",
    "$70,000 to $79,999",
    "$80,000 to $89,999",
    "$90,000 to $99,999",
    "$100,000 to $149,999",
    "$150,000 to $199,999",
    "$200,000 to $249,999",
    "$250,000 to $299,999",
    "$300,000 or more"
  )))

```


```{r, echo=FALSE}
# -- End preprocessing -- #
```

# Correlations with PAQ
```{r, message=FALSE}
model_and_plot <- function(outcome, predictor, df = df_proc){
  df %>% 
    mutate_at(vars(one_of(outcome, predictor)), ~as.vector(unlist(scale(.)))) %>% 
    lm(formula(glue("{outcome} ~ {predictor}")), data=.) %>% 
    summary %>% 
    print
  df %>% 
    ggplot(aes_string(x = predictor, y = outcome)) +
    geom_point(size = .7, alpha = .3) +
    geom_smooth(method = "lm", formula=y~x) 
}
```


## Well being
```{r, message=FALSE}
model_and_plot("swl", "paq")
model_and_plot("fm", "paq")
model_and_plot("panas_pos", "paq")
```

## Ill being
```{r, message=FALSE}
model_and_plot("panas_neg", "paq")
model_and_plot("pss", "paq")

df_proc %>% 
  lm(paq_sc ~ high_ace, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = high_ace, y = paq)) +
  stat_summary(fun.data = "mean_cl_boot")
```

## SES
```{r, message=FALSE}
ordinal::clm(income ~ paq_sc, data=df_proc) %>% 
  summary
model_and_plot("macarthur_us_rung", "paq")
model_and_plot("macarthur_comm_rung", "paq")
df_proc %>% 
  lm(paq_sc ~ race_white, .) %>% 
  summary
df_proc %>% 
  mutate(is_minority = ifelse(race_chicano | race_black, TRUE, FALSE)) %>% 
  lm(paq_sc ~ is_minority, .) %>% 
  summary
```

## Social desirability 
```{r, message=FALSE}
model_and_plot("sds", "paq")
```

## Fear of coronavirus
```{r, message=FALSE}
model_and_plot("fcv", "paq")
```

## Nature exposure
```{r, message=FALSE}
model_and_plot("nature_time", "paq")
model_and_plot("nature_freq", "paq")
```

## Emotion regulation
### Situation focused
```{r, message=FALSE}
model_and_plot("pmerq_sitsel_dis", "paq")
model_and_plot("pmerq_sitsel_eng", "paq")

model_and_plot("pmerq_sitmod_dis", "paq")
model_and_plot("pmerq_sitmod_eng", "paq")
```

### Attention
```{r, message=FALSE}
model_and_plot("pmerq_attdep", "paq")
model_and_plot("pmerq_attdep_dis", "paq")
model_and_plot("pmerq_attdep_eng", "paq")
model_and_plot("rrs_brood", "paq")
```

### Reappraisal
```{r, message=FALSE}
model_and_plot("pmerq_reappraise", "paq") 
model_and_plot("pmerq_repurp_dis", "paq") 
model_and_plot("pmerq_repurp_eng", "paq") 
model_and_plot("pmerq_recons_dis", "paq") 
model_and_plot("pmerq_recons_eng", "paq") 
```

### Response focused
```{r, message=FALSE}
model_and_plot("pmerq_respmod_dis", "paq") 
model_and_plot("pmerq_respmod_eng", "paq") 
```

# Correlations with TAS
## Emotion regulation
### Situation focused
```{r, message=FALSE}
model_and_plot("pmerq_sitsel_dis", "tas")
model_and_plot("pmerq_sitsel_eng", "tas")
model_and_plot("pmerq_sitmod_dis", "tas")
model_and_plot("pmerq_sitmod_eng", "tas")
```

### Attention
```{r, message=FALSE}
model_and_plot("pmerq_attdep", "tas")
model_and_plot("pmerq_attdep_dis", "tas")
model_and_plot("pmerq_attdep_eng", "tas")
model_and_plot("rrs_brood", "tas")
```

### Reappraisal
```{r, message=FALSE}
model_and_plot("pmerq_reappraise", "tas") 
model_and_plot("pmerq_repurp_dis", "tas") 
model_and_plot("pmerq_repurp_eng", "tas") 
model_and_plot("pmerq_recons_dis", "tas") 
model_and_plot("pmerq_recons_eng", "tas") 
```

### Response focused
```{r, message=FALSE}
model_and_plot("pmerq_respmod_dis", "tas") 
model_and_plot("pmerq_respmod_eng", "tas") 
```

# Correlations of ER and well-being
## Situation selection
```{r, message=FALSE}
model_and_plot("pmerq_sitsel_dis", "fm")
model_and_plot("pmerq_sitsel_dis", "panas_pos")
model_and_plot("pmerq_sitsel_dis", "swl")

model_and_plot("pmerq_sitsel_eng", "fm")
model_and_plot("pmerq_sitsel_eng", "panas_pos")
model_and_plot("pmerq_sitsel_eng", "swl")
```

## Situation modification
```{r, message=FALSE}
model_and_plot("pmerq_sitmod_dis", "fm")
model_and_plot("pmerq_sitmod_dis", "panas_pos")
model_and_plot("pmerq_sitmod_dis", "swl")

model_and_plot("pmerq_sitmod_eng", "fm")
model_and_plot("pmerq_sitmod_eng", "panas_pos")
model_and_plot("pmerq_sitmod_eng", "swl")
```

### Attention
```{r, message=FALSE}
model_and_plot("pmerq_attdep_dis", "fm")
model_and_plot("pmerq_attdep_dis", "panas_pos")
model_and_plot("pmerq_attdep_dis", "swl")

model_and_plot("pmerq_attdep_eng", "fm")
model_and_plot("pmerq_attdep_eng", "panas_pos")
model_and_plot("pmerq_attdep_eng", "swl")

model_and_plot("rrs_brood", "fm")
model_and_plot("rrs_brood", "fm")
model_and_plot("rrs_brood", "fm")
```

### Reappraisal
```{r, message=FALSE}
model_and_plot("pmerq_reappraise", "fm") 
model_and_plot("pmerq_repurp_dis", "fm") 
model_and_plot("pmerq_repurp_eng", "fm") 
model_and_plot("pmerq_recons_dis", "fm") 
model_and_plot("pmerq_recons_eng", "fm") 
```

### Response focused
```{r, message=FALSE}
model_and_plot("pmerq_respmod_dis", "fm") 
model_and_plot("pmerq_respmod_eng", "fm") 
```

# Correlations of ER and ill-being
## Situation selection
```{r, message=FALSE}
model_and_plot("pmerq_sitsel_dis", "pss")
model_and_plot("pmerq_sitsel_dis", "panas_neg")

model_and_plot("pmerq_sitsel_eng", "pss")
model_and_plot("pmerq_sitsel_eng", "panas_neg")
```

## Situation modification
```{r, message=FALSE}
model_and_plot("pmerq_sitmod_dis", "pss")
model_and_plot("pmerq_sitmod_dis", "panas_neg")

model_and_plot("pmerq_sitmod_eng", "pss")
model_and_plot("pmerq_sitmod_eng", "panas_neg")
```

### Attention
```{r, message=FALSE}
model_and_plot("pmerq_attdep_dis", "pss")
model_and_plot("pmerq_attdep_dis", "panas_neg")

model_and_plot("pmerq_attdep_eng", "pss")
model_and_plot("pmerq_attdep_eng", "panas_neg")

model_and_plot("rrs_brood", "pss")
model_and_plot("rrs_brood", "panas_neg")
```

### Reappraisal
```{r, message=FALSE}
model_and_plot("pmerq_reappraise", "pss") 
model_and_plot("pmerq_reappraise", "panas_neg") 

model_and_plot("pmerq_repurp_dis", "pss") 
model_and_plot("pmerq_repurp_dis", "panas_neg")

model_and_plot("pmerq_repurp_eng", "pss") 
model_and_plot("pmerq_repurp_eng", "panas_neg") 

model_and_plot("pmerq_recons_dis", "pss") 
model_and_plot("pmerq_recons_dis", "panas_neg") 

model_and_plot("pmerq_recons_eng", "pss") 
model_and_plot("pmerq_recons_eng", "panas_neg") 
```

### Response focused
```{r, message=FALSE}
model_and_plot("pmerq_respmod_dis", "pss") 
model_and_plot("pmerq_respmod_dis", "panas_neg") 

model_and_plot("pmerq_respmod_eng", "pss") 
model_and_plot("pmerq_respmod_eng", "panas_neg") 
```



<!-- # Webb SS moderation with PAQ -->

