---
title: "Nature ER National Qualtrics Study"
author: "Ashish and Jordan"
date: "`r Sys.Date()`"
output: rmdformats::readthedown
params:
  inputdatafile: ""
---

# Notes
## TODO 
* Need to figure out how to deal with heteroscedasticity for time in nature. E.g. in mediation models
  * Lim & Melville. (2009). Robustness of Structural Equation Modeling to Distributional Misspecification: Empirical Evidence & Research Guidelines 

# Initialization
```{r, message=FALSE}
library(lavaan)
library(lmerTest)
library(here)
library(tidyverse)
library(glue)
library(tidylog)
require(rmdformats)
theme_set(theme_bw())
```

# Preprocessing 
## Functions
```{r}
scale <- function(...){as.vector(unlist(base::scale(...)))}
```


## Read data
```{r, message=F}

data_filepath <- params$inputdatafile
df_file <- read_csv(here(data_filepath))
df_proc <- df_file %>% 
  mutate(hi_ace = as.factor(high_ace))

```



```{r, echo=FALSE}
# ------ End Preprocessing ------ #
# ----- Run all chunks above -----#
```

# Preregistration 

## Hypotheses

[Pre-registration](https://osf.io/t94h2) 

1A. We hypothesize that nature contact will be associated with greater frequency of (i) situation selection in the form of approaching positively valenced situations, (ii) distraction, and (iii) reappraisal strategies and (iv) lesser frequency of rumination. Moreover, we hypothesize that emotion regulation strategies will be related to affective outcomes.

1B. We hypothesize that frequency of distraction, reappraisal, and rumination will mediate the association of nature contact with affective outcomes.

2A. We hypothesize that nature contact will moderate the associations of (i) adverse life experiences and (ii) perceived social status with affective outcomes.

2B. We hypothesize that these moderations will be mediated by frequency of reappraisal and rumination.

## Statistical analysis 

Multiple regression models will test whether time with nature predicts positive affect, negative affect, and emotion regulation (reappraisal, rumination, suppression); and whether situation selection predicts time with nature; controlling for fear of COVID-19, Nature Relatedness, and age/demographic covariates. We will use model comparison procedures (i.e. LR-test and AIC/BIC) to determine whether covariates improve model fit and include them in the final model contingent on this procedure. Multiple regression analysis will also allow for us to test whether the relationship between ACE scores and perceived social status with affect is moderated by time with nature.

Structural equation modeling will be used to test whether emotion regulation mediates the association of time with nature with affective outcomes. We will evaluate bootstrapped confidence intervals for indirect effects to determine significance of mediation.

## Data exclusion

Participants must pass 4/4 attention checks to be included.

Following Leiner (2019), we will remove participants based on implausible completion times using the following procedure: "For each page, the sample’s median page completion time is divided by the individual completion time, resulting in a speed factor. A factor of 2 means that the respondent has completed a page twice as fast as the typical respondent. An average speed factor per respondent is computed after the page factors are clipped to a maximum value of 3."
We will exclude participants who respond with an average speed factor greater than 2.

Sensitivity analyses will be run to compare results with and without outliers.

# Distributions 

##  Total N
```{r, message=F}
df_proc %>% 
  nrow
df_proc %>% 
  pull(pid) %>% 
  unique %>% 
  length
```

## Demographics

### Gender
```{r, message=F}
df_proc %>% 
  group_by(gender) %>% 
  summarize(n = n())
```

### Age
```{r, message=F}
df_proc %>% 
  ggplot(aes(x = age)) + 
  geom_histogram(binwidth = 10) + 
  labs(x = "Age", y = "count") + 
  ggtitle("Age histogram")

# Get mean age and standard deviation
df_proc %>% 
  summarize(mean_age = mean(age, na.rm = T),
            sd_age = sd(age, na.rm = T))

```


### MacArthur status
```{r, message=F}
# MacArthur US histogram
df_proc %>%
  ggplot(aes(x=macarthur_us_rung))+
  geom_histogram(binwidth = 1) +
  labs(x = "MacArthur Rung US", y = "count") +
  ggtitle("MacArthur Rung US histogram")

# MacArthur community histogram
df_proc %>%
  ggplot(aes(x=macarthur_comm_rung))+
  geom_histogram(binwidth = 1) +
  labs(x = "MacArthur Rung Community", y = "count") +
  ggtitle("MacArthur Rung Community histogram")
```

### Education
```{r, message=F}
df_proc %>% 
  ggplot(aes(x = edu)) + 
  geom_bar() +
  labs(x = "Education", y = "count") +
  coord_flip() # rotate the plot
```

### Income
```{r, message=F}
df_proc %>%
  ggplot(aes(x = income)) + 
  geom_bar() + 
  labs(x = "Income", y = "count") +
  coord_flip()
```

### Race

```{r, message=F}
df_race <- df_proc %>% 
  select(pid, starts_with("race_")) %>% 
  select(-race_text) %>% 
  pivot_longer(!pid, names_to = "race") %>% 
  group_by(race) %>% 
  summarize(n = sum(value),
            pr = mean(value)) %>% 
  mutate(race = str_replace(race, "race_", "")) %>% 
  arrange(n) %>% 
  mutate(race = fct_reorder(race, n))
    
df_race %>% 
  knitr::kable()
df_race %>% 
  ggplot(aes(x = race, y = n)) +
  geom_bar(stat="identity") +
  coord_flip()
  
```

## Time in nature 
> Over the last month, approximately how many HOURS PER WEEK do you consider yourself to have interacted with nature? This includes, for example, walking, biking, or recreating outside in local, regional, or national parks, at the beach, beside or within lakes, creeks, or the ocean, gardening or tending to plants, camping, fishing, reading or walking outside next to trees, engaging in yard work with natural elements, etc...

* Highly skewed distribution

```{r, message=F}

df_proc %>% 
  ggplot(aes(x = nature_time)) + 
  geom_histogram(binwidth = 5) + 
  labs(x = "hours/week in nature", y = "count") + 
  ggtitle("Hours/week in nature histogram")

df_proc %>% 
  ggplot(aes(x = nature_time_log)) + 
  geom_histogram(binwidth = 0.5) +
  labs(x = "log transformed hours/week in nature", y = "count") + 
  ggtitle("Log-transformed hours/week in nature histogram")
```

## Frequency of nature contact
> About how often do you usually visit or pass through outdoor natural areas for any reason? This includes, for example, walking, biking, or recreating outside in local, regional, or national parks, at the beach, beside or within lakes, creeks, or the ocean, gardening or tending to plants, camping, fishing, reading or walking outside next to trees, engaging in yard work with natural elements, etc...

```{r, message=F}
df_proc %>%
  ggplot(aes(x = nature_freq_factor)) + 
  geom_bar() +
  labs(x = "frequency of nature contact", y = "count") +
  ggtitle("Frequency of nature contact histogram") +
  coord_flip()
```

## Nature setting
> Which option best describes where, in the past month, most of your nature exposure took place? If you spent time in multiple nature areas, please pick the option where you spent the most time. 

```{r, message=F}
df_proc %>%
  ggplot(aes(x = nature_setting)) +
  geom_bar() +
  labs(x = "nature setting", y = "count") +
  ggtitle("Nature setting histogram") +
  coord_flip()
```

## Perceived exertion in nature
> Please rate your perception of exertion, i.e. how heavy and strenuous the exercise felt to you and how tired you were, when you were in the natural area during which you spent the most time in the past month. The perception of exertion is mainly felt as strain and fatigue in your muscles and as breathlessness or aches in the chest. Use this scale from 6 to 20, where 6 means “No exertion at all” and 20
means “Maximal exertion.”

```{r, message=F}
df_proc %>%
  ggplot(aes(x = perceived_exertion)) +
  geom_histogram(binwidth = 1) +
  labs(x = "perceived exertion", y = "count") +
  ggtitle("Perceived exertion in nature histogram")
```



## Situation selection frequency 

Vars: 
* sitselect 
* sitselect_approach
* sitselect_avoid 
* pmerq_sitsel_eng 
* pmerq_sitsel_dis 
```{r, message=F}

df_proc %>%
  ggplot(aes(x = sitselect)) +
  geom_histogram(binwidth = 1) +
  labs(x = "situation selection", y = "count") +
  ggtitle("Situation selection histogram")

df_proc %>%
  ggplot(aes(x = sitselect_approach)) +
  geom_histogram(binwidth = 1) +
  labs(x = "situation selection approach", y = "count") +
  ggtitle("Situation selection approach histogram")

  df_proc %>%
  ggplot(aes(x = sitselect_avoid)) +
  geom_histogram(binwidth = 1) +
  labs(x = "situation selection avoid", y = "count") +
  ggtitle("Situation selection avoid histogram")

df_proc %>%
  ggplot(aes(x = pmerq_sitsel_eng)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ situation selection engagement", y = "count") +
  ggtitle("PMERQ situation selection engagement histogram")

df_proc %>%
  ggplot(aes(x = pmerq_sitsel_dis)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ situation selection disengagement", y = "count") +
  ggtitle("PMERQ situation selection disengagement histogram")
```

## Situation modification frequency

Vars: 
* pmerq_sitmod_eng 
* pmerq_sitmod_dis 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = pmerq_sitmod_eng)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ situation modification engagement", y = "count") +
  ggtitle("PMERQ situation modification engagement histogram")

df_proc %>%
  ggplot(aes(x = pmerq_sitmod_dis)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ situation modification disengagement", y = "count") +
  ggtitle("PMERQ situation modification disengagement histogram")
```

## Distraction frequency

Vars: 
* pmerq_attdep 
* pmerq_attdep_eng 
* pmerq_attdep_dis 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = pmerq_attdep)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ attention deployment", y = "count") +
  ggtitle("PMERQ attention deployment histogram")

df_proc %>%
  ggplot(aes(x = pmerq_attdep_eng)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ attention deployment engagement", y = "count") +
  ggtitle("PMERQ attention deployment engagement histogram")

df_proc %>%
  ggplot(aes(x = pmerq_attdep_dis)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ attention deployment disengagement", y = "count") +
  ggtitle("PMERQ attention deployment disengagement histogram")
```

## Rumination frequency 

Vars: 
* rrs_brood 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = rrs_brood)) +
  geom_histogram(binwidth = 1) +
  labs(x = "ruminative response brooding", y = "count") +
  ggtitle("Brooding (Rumination Reponse Scale) histogram")
```

## Reappraisal frequency 

Vars:
* pmerq_reappraise 
* pmerq_recons 
* pmerq_recons_eng
* pmerq_recons_dis
* pmerq_repurp 
* pmerq_repurp_eng  
* pmerq_repurp_dis 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = pmerq_reappraise)) +
  geom_histogram(binwidth = 5) +
  labs(x = "PMERQ reappraisal", y = "count") +
  ggtitle("PMERQ reappraisal histogram")

df_proc %>%
  ggplot(aes(x = pmerq_recons)) +
  geom_histogram(binwidth = 2) +
  labs(x = "PMERQ reconstrual", y = "count") +
  ggtitle("PMERQ reconstrual histogram")

df_proc %>%
  ggplot(aes(x = pmerq_recons_eng)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ reconstrual engagement", y = "count") +
  ggtitle("PMERQ reconstrual engagement histogram")

df_proc %>%
  ggplot(aes(x = pmerq_recons_dis)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ reconstrual disengagement", y = "count") +
  ggtitle("PMERQ reconstrual disengagement histogram")

df_proc %>%
  ggplot(aes(x = pmerq_repurp)) +
  geom_histogram(binwidth = 2) +
  labs(x = "PMERQ repurposing", y = "count") +
  ggtitle("PMERQ repurposing histogram")

df_proc %>%
  ggplot(aes(x = pmerq_repurp_eng)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ repurposing engagement", y = "count") +
  ggtitle("PMERQ repurposing engagement histogram")

df_proc %>%
  ggplot(aes(x = pmerq_repurp_dis)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ repurposing disengagement", y = "count") +
  ggtitle("PMERQ repurposing disengagement histogram")
```

## Suppression frequency 

Vars:
* pmerq_respmod_dis 

```{r, message=F}
df_proc %>%
  ggplot(aes(x = pmerq_respmod_dis)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ response modulation disengagement", y = "count") +
  ggtitle("Suppression frequency histogram")
```

## Social support frequency 

Vars:
* pmerq_respmod_eng  
```{r, message=F}
df_proc %>%
  ggplot(aes(x = pmerq_respmod_eng)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ response modulation engagement", y = "count") +
  ggtitle("Social support histogram")
```


## Flourishing 

Vars:
* fm
```{r, message=F}
df_proc %>%
  ggplot(aes(x = fm)) +
  geom_histogram(binwidth = 5) +
  labs(x = "flourishing measure score", y = "count") +
  ggtitle("Flourishing histogram")
```

## Satisfaction with life 

Vars:
* swl 
```{r, message=F}

df_proc %>%
  ggplot(aes(x = swl)) +
  geom_histogram(binwidth = 1) +
  labs(x = "satisfaction with life score", y = "count") +
  ggtitle("Satisfaction with life histogram")
```

## Positive affect (PANAS)

Vars: 
* panas_pos 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = panas_pos)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PANAS positive affect score", y = "count") +
  ggtitle("PANAS positive affect histogram")
```

## ACE

Vars: 
* ACE
```{r, message=F}
df_proc %>%
  ggplot(aes(x = ace)) +
  geom_histogram(binwidth = 1)
df_proc %>% 
  ggplot(aes(x = hi_ace)) +
  geom_bar()
```

## Negative affect (PANAS) 

Vars: 
* panas_neg 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = panas_neg)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PANAS negative affect score", y = "count") +
  ggtitle("PANAS negative affect histogram")
```

## Perceived Stress 

Vars:
* pss 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = pss)) +
  geom_histogram(binwidth = 1) +
  labs(x = "Perceived Stress Scale score", y = "count") +
  ggtitle("Perceived stress histogram")
```


## Alexithymia PAQ 

Vars: 
* paq 
* paq_dif 
* paq_ddf 
* paq_eot 
* paq_pos 
* paq_neg 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = paq)) +
  geom_histogram(binwidth = 5) +
  labs(x = "PAQ score", y = "count") +
  ggtitle("PAQ histogram")

df_proc %>%
  ggplot(aes(x = paq_dif)) +
  geom_histogram(binwidth = 3) +
  labs(x = "PAQ difficulty identifying feelings score", y = "count") +
  ggtitle("PAQ difficulty identifying feelings histogram")

df_proc %>%
  ggplot(aes(x = paq_ddf)) +
  geom_histogram(binwidth = 3) +
  labs(x = "PAQ difficulty describing feelings score", y = "count") +
  ggtitle("PAQ difficulty describing feelings histogram")

df_proc %>%
  ggplot(aes(x = paq_eot)) +
  geom_histogram(binwidth = 3) +
  labs(x = "PAQ externally oriented thinking score", y = "count") +
  ggtitle("PAQ externally oriented thinking histogram")

df_proc %>%
  ggplot(aes(x = paq_pos)) +
  geom_histogram(binwidth = 3) +
  labs(x = "PAQ positive score", y = "count") +
  ggtitle("PAQ positive histogram")

df_proc %>%
  ggplot(aes(x = paq_neg)) +
  geom_histogram(binwidth = 3) +
  labs(x = "PAQ negative score", y = "count") +
  ggtitle("PAQ negative histogram")
```

## Alexithymia TAS 

Vars: 
* tas 
* tas_dif 
* tas_ddf 
* tas_eot
```{r, message=F}
df_proc %>%
  ggplot(aes(x = tas)) +
  geom_histogram(binwidth = 2) +
  labs(x = "TAS total score", y = "count") +
  ggtitle("TAS total score histogram")

df_proc %>%
  ggplot(aes(x = tas_dif)) +
  geom_histogram(binwidth = 1) +
  labs(x = "TAS difficulty identifying feelings score", y = "count") +
  ggtitle("TAS difficulty identifying feelings histogram")

df_proc %>%
  ggplot(aes(x = tas_ddf)) +
  geom_histogram(binwidth = 1) +
  labs(x = "TAS difficulty describing feelings score", y = "count") +
  ggtitle("TAS difficulty describing feelings histogram")

df_proc %>%
  ggplot(aes(x = tas_eot)) +
  geom_histogram(binwidth = 1) +
  labs(x = "TAS externally oriented thinking score", y = "count") +
  ggtitle("TAS externally oriented thinking histogram")
```


## Fear of coronavirus 

Vars: 
* fcv 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = fcv)) +
  geom_histogram(binwidth = 1) +
  labs(x = "fear of coronavirus scale score", y = "count") +
  ggtitle("Fear of coronavirus histogram")
```

## Social desiribility 

Vars: 
* sds 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = sds)) +
  geom_histogram(binwidth = 1) +
  labs(x = "social desiribility scale score", y = "count") +
  ggtitle("Social desiribility histogram")
```


# Confirmatory analyses

In these headings of these Confirmatory analyses, asteriks indicate significance of a hypothesized effect. 

† => p < .10 

\* => p < .05 

\*\* => p < .01 

\*\*\* => p < .001


# H1a: Nature contact and ER frequency 
We hypothesize that nature contact will be associated with greater frequency of (i) situation selection in the form of approaching positively valenced situations, (ii) distraction, and (iii) reappraisal strategies and (iv) lesser frequency of rumination. Moreover, we hypothesize that emotion regulation strategies will be related to affective outcomes. 

## * Nature time <-> situation selection approach pos

* Heteroscedasticity 

```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>%
  lm(sitselect_approach ~ nature_time, .) %>% 
  summary

df_proc %>% 
  ggplot(aes(x = sitselect_approach, y = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```


## Nature time <-> distraction 
```{r}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(pmerq_attdep_dis ~ nature_time, .) %>% 
  summary

df_proc %>% 
  ggplot(aes(x = pmerq_attdep_dis, y = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```



## ** Nature time <-> reappraisal 
```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(pmerq_reappraise ~ nature_time, .) %>% 
  summary

df_proc %>% 
  ggplot(aes(x = pmerq_reappraise, y = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## † Nature time <-> rumination 
```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(rrs_brood ~ nature_time, .) %>% 
  summary

df_proc %>% 
  ggplot(aes(x = rrs_brood, y = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## ** Nature time <-> flourishing 
```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(fm ~ nature_time, .) %>% 
  summary

df_proc %>% 
  ggplot(aes(x = fm, y = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## *** Nature time <-> satisfaction with life 
```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(swl ~ nature_time, .) %>% 
  summary

df_proc %>% 
  ggplot(aes(y = swl, x = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## Nature time <-> perceived stress 
```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(pss ~ nature_time, .) %>% 
  summary


df_proc %>% 
  ggplot(aes(x = pss, y = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## *** Nature time <-> positive affect 
```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(panas_pos ~ nature_time, .) %>% 
  summary

df_proc %>% 
  ggplot(aes(x = panas_pos, y = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## Nature freq <-> negative affect 
```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(panas_neg ~ nature_freq, .) %>% 
  summary

df_proc %>% 
  ggplot(aes(x = panas_neg, y = nature_freq)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## *** Nature freq <-> sitselect_approach
```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(sitselect_approach ~ nature_freq, .) %>% 
  summary

df_proc %>% 
  ggplot(aes(x = sitselect_approach, y = nature_freq)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```


## Nature freq <-> distraction 
```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(pmerq_attdep_dis ~ nature_freq, .) %>% 
  summary

df_proc %>% 
  ggplot(aes(x = pmerq_attdep_dis, y = nature_freq)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## *** Nature freq <-> reappraisal 
```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(pmerq_reappraise ~ nature_freq, .) %>% 
  summary

df_proc %>% 
  ggplot(aes(x = pmerq_reappraise, y = nature_freq)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## ** Nature freq <-> rumination 
```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(rrs_brood ~ nature_freq, .) %>% 
  summary

df_proc %>% 
  ggplot(aes(x = rrs_brood, y = nature_freq)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## ** Nature freq <-> flourishing 
```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(fm ~ nature_freq, .) %>% 
  summary

df_proc %>% 
  ggplot(aes(x = fm, y = nature_freq)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## *** Nature freq <-> satisfaction with life 
```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(swl ~ nature_freq, .) %>% 
  summary


df_proc %>% 
  ggplot(aes(y = swl, x = nature_freq)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## Nature freq <-> perceived stress 
```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(pss ~ nature_freq, .) %>% 
  summary

df_proc %>% 
  ggplot(aes(x = pss, y = nature_freq)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## *** Nature freq <-> positive affect 
```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(panas_pos ~ nature_freq, .) %>% 
  summary

df_proc %>% 
  ggplot(aes(x = panas_pos, y = nature_freq)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## Nature freq <-> negative affect 
```{r, message=F}
df_proc %>% 
  mutate_if(is.numeric, scale) %>% 
  lm(panas_neg ~ nature_freq, .) %>% 
  summary

df_proc %>% 
  ggplot(aes(x = panas_neg, y = nature_freq)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```



# H1b: Nature exposure -> ER -> affect 
We hypothesize that frequency of distraction, reappraisal, and rumination will mediate the association of nature contact with affective outcomes.

```{r}
run_mediation <- function(a, b, c, ...){
  mod <- glue('
{b} ~ a*{a}
{c} ~ b*{b} + cp*{a}
indirect := a*b
total := indirect + cp
')
  fit <- sem(mod, ...)
  
  parameterEstimates(
    fit,
    boot.ci.type="bca.simple",
    level=0.95,
    ci=TRUE,
    standardized = TRUE
  ) %>% 
    as.data.frame %>% 
    dplyr::mutate_if(is.numeric, ~round(., 3)) %>% 
    select(-std.lv, -std.nox) %>% 
    knitr::kable() %>% 
    print
  
  return(fit)
}

```


## Nature time -> Rumination -> Positive affect 
* Non-significant indirect effect
```{r, message=F}
fit <- run_mediation("nature_time", 
                     "rrs_brood", 
                     "panas_pos",
              se="bootstrap",
              data=df_proc)

```

## Nature time -> Distraction -> Positive affect 

* Non-significant indirect effect
```{r, message=F}

fit <- run_mediation("nature_time", 
                     "pmerq_attdep_dis", 
                     "panas_pos",
              se="bootstrap",
              data=df_proc)

```

## ** Nature time -> Reappraisal -> Positive affect 

```{r, message=F}
fit <- run_mediation("nature_time", 
                     "pmerq_reappraise", 
                     "panas_pos",
              se="bootstrap",
              data=df_proc)

```

## Nature time -> Rumination -> Flourishing 

* Non-significant indirect effect 
```{r, message=F}
fit <- run_mediation("nature_time", 
                     "rrs_brood", 
                     "fm",
              se="bootstrap",
              data=df_proc)

```

## Nature time -> Distraction -> Flourishing 

* Non-significant indirect effect 
```{r, message=F}

fit <- run_mediation("nature_time", 
                     "pmerq_attdep_dis", 
                     "fm",
              se="bootstrap",
              data=df_proc)

```

## ** Nature time -> Reappraisal -> Flourishing 

```{r, message=F}

fit <- run_mediation("nature_time", 
                     "pmerq_reappraise", 
                     "fm",
              se="bootstrap",
              data=df_proc)

```

## Nature time -> Rumination -> Satisfaction with life

* Non-significant indirect effect 
```{r, message=F}

fit <- run_mediation("nature_time", 
                     "rrs_brood", 
                     "swl",
              se="bootstrap",
              data=df_proc)

```

## Nature time -> Distraction -> Satisfaction with life 

* Non-significant indirect effect 
```{r, message=F}
fit <- run_mediation("nature_time", 
                     "pmerq_attdep_dis", 
                     "swl",
              se="bootstrap",
              data=df_proc)
```

## ** Nature time -> Reappraisal -> Satisfaction with life 

```{r, message=F}

fit <- run_mediation("nature_time", 
                     "pmerq_reappraise", 
                     "swl",
              se="bootstrap",
              data=df_proc)

```

## Nature freq -> Reappraisal -> Flourishing
```{r}
fit <- run_mediation("nature_time", 
                     "pmerq_reappraise", 
                     "fm",
              se="bootstrap",
              data=df_proc)
```

## Nature freq -> Reappraisal -> Satisfaction with life
```{r}
fit <- run_mediation("nature_time", 
                     "pmerq_reappraise", 
                     "swl",
              se="bootstrap",
              data=df_proc)
```

## Nature freq -> Reappraisal -> Positive affect
```{r}
fit <- run_mediation("nature_time", 
                     "pmerq_reappraise", 
                     "panas_pos",
              se="bootstrap",
              data=df_proc)
```

## Nature freq -> Rumination -> Flourishing
```{r}
fit <- run_mediation("nature_time", 
                     "rrs_brood", 
                     "fm",
              se="bootstrap",
              data=df_proc)
```

## Nature freq -> Rumination -> Satisfaction with life
```{r}
fit <- run_mediation("nature_time", 
                     "rrs_brood", 
                     "swl",
              se="bootstrap",
              data=df_proc)
```

## Nature freq -> Rumination -> Positive affect
```{r}
fit <- run_mediation("nature_time", 
                     "rrs_brood", 
                     "panas_pos",
              se="bootstrap",
              data=df_proc)
```

# H2a: Nature contact moderates association of adverse experience and affect 

We hypothesize that nature contact will moderate the associations of (i) adverse life experiences and (ii) perceived social status with affective outcomes. 

## † Nature time x ACE -> Positive affect 

* marginally significant when using binary ACE 
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(panas_pos ~ nature_time * ace, .) %>% 
  summary
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(panas_pos ~ nature_time * hi_ace, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = panas_pos, color = hi_ace)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Positive affect (PANAS-pos)", color = "High ACE") 
```

## Nature time x ACE -> Flourishing 
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(fm ~ nature_time * ace, .) %>% 
  summary
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(fm ~ nature_time * hi_ace, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = fm, color = hi_ace)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Flourishing (fm)", color = "High ACE") 
```

## Nature time x ACE -> Satisfaction with life  
```{r, message=F}

df_proc %>%
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(swl ~ nature_time * ace, .) %>%
  summary
df_proc %>%
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(swl ~ nature_time * hi_ace, .) %>%
  summary
df_proc %>%
  ggplot(aes(x = nature_time, y = swl, color = hi_ace)) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Satisfaction with life (swl)", color = "High ACE")
```

## † Nature time x ACE -> Negative affect 

* marginally significant when using binary ACE 
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(panas_neg ~ nature_time * ace, .) %>% 
  summary
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(panas_neg ~ nature_time * hi_ace, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = panas_neg, color = hi_ace)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Negative affect (PANAS-neg)", color = "High ACE") 
```


## Nature time x ACE -> Perceived stress 
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(pss ~ nature_time * ace, .) %>% 
  summary
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(pss ~ nature_time * hi_ace, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = pss, color = hi_ace)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Perceived stress (pss)", color = "High ACE") 
```

## Nature time x Macarthur US -> Positive affect
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%   
  lm(panas_pos ~ nature_time * macarthur_us_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = panas_pos, color = factor(high_macarthur_us_rung))) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Positive affect (PANAS-pos)", color = "High Macarthur US status") 
```

## Nature time x Macarthur US -> Flourishing 
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%   
  lm(fm ~ nature_time * macarthur_us_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = fm, color = factor(high_macarthur_us_rung))) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Flourishing  (fm)", color = "High Macarthur US status") 
```

## * Nature time x Macarthur US -> Satisfaction with life  
```{r, message=F}

df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%  
  lm(swl ~ nature_time * macarthur_us_rung, .) %>%
  summary
df_proc %>%
  ggplot(aes(x = nature_time, y = swl, color = factor(high_macarthur_us_rung))) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Satisfaction with life (swl)", color = "High Macarthur US status")
```

## Nature time x Macarthur US -> Negative affect   
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%   
  lm(panas_neg ~ nature_time * macarthur_us_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = panas_neg, color = factor(high_macarthur_us_rung))) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Negative affect (PANAS-neg)", color = "High Macarthur US status") 
```

## Nature time x Macarthur US -> Perceived stress 
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%   
  lm(pss ~ nature_time * macarthur_us_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = pss, color = factor(high_macarthur_us_rung))) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Perceived stress (pss)", color = "High Macarthur US status") 
```

## Nature time x Macarthur Community -> Positive affect
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%   
  lm(panas_pos ~ nature_time * macarthur_comm_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = panas_pos, 
             color = factor(high_macarthur_comm_rung))) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Positive affect (PANAS-pos)", color = "High Macarthur Community status") 
```

## Nature time x Macarthur Community -> Flourishing 
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%   
  lm(fm ~ nature_time * macarthur_comm_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = fm, 
             color = factor(high_macarthur_comm_rung))) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Flourishing (fm)", color = "High Macarthur Community status") 
```

## Nature time x Macarthur Community -> Satisfaction with life  
```{r, message=F}

df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%  
  lm(swl ~ nature_time * macarthur_comm_rung, .) %>%
  summary
df_proc %>%
  ggplot(aes(x = nature_time, y = swl, 
             color = factor(high_macarthur_comm_rung))) + 
  geom_point(alpha = .3) +
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Satisfaction with life (swl)", color = "High Macarthur Community status")
```

## Nature time x Macarthur Community -> Negative affect   
```{r, message=F}
df_proc %>%
  dplyr::mutate_if(is.numeric, scale) %>%   
  lm(panas_neg ~ nature_time * macarthur_comm_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = panas_neg, 
             color = factor(high_macarthur_comm_rung))) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Negative affect (PANAS-neg)", color = "High Macarthur Community status") 
```

## Nature time x Macarthur Community -> Perceived stress 
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%   
  lm(pss ~ nature_time * macarthur_comm_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = pss,
             color = factor(high_macarthur_comm_rung))) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Perceived stress (pss)", color = "High Macarthur Community status") 
```

## Nature freq x ACE -> Positive affect 
```{r, message=F}
df_proc %>%
  dplyr::mutate_if(is.numeric, scale) %>%   
  lm(panas_pos ~ nature_freq * ace, .) %>% 
  summary
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(panas_pos ~ nature_freq * hi_ace, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_freq, y = panas_pos, color = hi_ace)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Nature frequency", y = "Positive affect (PANAS-pos)", color = "High ACE") 
```

## † Nature freq x ACE -> Flourishing 

* marginally significant using binary ace

```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(fm ~ nature_freq * ace, .) %>% 
  summary
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(fm ~ nature_freq * hi_ace, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_freq, y = fm, color = hi_ace)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Nature frequency", y = "Flourishing (fm)", color = "High ACE") 
```

## ** Nature freq x ACE -> Satisfaction with life  
```{r, message=F}

df_proc %>%
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(swl ~ nature_freq * ace, .) %>%
  summary
df_proc %>%
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(swl ~ nature_freq * hi_ace, .) %>%
  summary
df_proc %>%
  ggplot(aes(x = nature_freq, y = swl, color = hi_ace)) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm") +
  labs(x = "Nature frequency", y = "Satisfaction with life (swl)", color = "High ACE")
```

## Nature freq x ACE -> Negative affect 

```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(panas_neg ~ nature_freq * ace, .) %>% 
  summary
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(panas_neg ~ nature_freq * hi_ace, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_freq, y = panas_neg, color = hi_ace)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Nature frequency", y = "Negative affect (PANAS-neg)", color = "High ACE") 
```


## Nature freq x ACE -> Perceived stress 
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(pss ~ nature_freq * ace, .) %>% 
  summary
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%
  lm(pss ~ nature_freq * hi_ace, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_freq, y = pss, color = hi_ace)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Nature frequency", y = "Perceived stress (pss)", color = "High ACE") 
```

## Nature freq x Macarthur US -> Positive affect
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>% 
  lm(panas_pos ~ nature_freq * macarthur_us_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_freq, y = panas_pos, color = factor(high_macarthur_us_rung))) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Nature frequency", y = "Positive affect (PANAS-pos)", color = "High Macarthur US status") 
```

## Nature freq x Macarthur US -> Flourishing 
```{r, message=F}
df_proc %>%
  dplyr::mutate_if(is.numeric, scale) %>%  
  lm(fm ~ nature_freq * macarthur_us_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_freq, y = fm, color = factor(high_macarthur_us_rung))) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Nature frequency", y = "Flourishing  (fm)", color = "High Macarthur US status") 
```

## Nature freq x Macarthur US -> Satisfaction with life  
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%  
  lm(swl ~ nature_freq * macarthur_us_rung, .) %>%
  summary
df_proc %>%
  ggplot(aes(x = nature_freq, y = swl, color = factor(high_macarthur_us_rung))) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm") +
  labs(x = "Nature frequency", y = "Satisfaction with life (swl)", color = "High Macarthur US status")
```

## ** Nature freq x Macarthur US -> Negative affect   
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%   
  dplyr::mutate_if(is.numeric, scale) %>% 
  lm(panas_neg ~ nature_freq * macarthur_us_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_freq, y = panas_neg, color = factor(high_macarthur_us_rung))) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Nature frequency", y = "Negative affect (PANAS-neg)", color = "High Macarthur US status") 
```

## ** Nature freq x Macarthur US -> Perceived stress 
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%   
  lm(pss ~ nature_freq * macarthur_us_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_freq, y = pss, color = factor(high_macarthur_us_rung))) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Nature frequency", y = "Perceived stress (pss)", color = "High Macarthur US status") 
```

## Nature freq x Macarthur Community -> Positive affect
```{r, message=F}
df_proc %>%
  dplyr::mutate_if(is.numeric, scale) %>%   
  lm(panas_pos ~ nature_freq * macarthur_comm_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_freq, y = panas_pos, 
             color = factor(high_macarthur_comm_rung))) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Nature frequency", y = "Positive affect (PANAS-pos)", color = "High Macarthur Community status") 
```

## Nature freq x Macarthur Community -> Flourishing 
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%   
  lm(fm ~ nature_freq * macarthur_comm_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_freq, y = fm, 
             color = factor(high_macarthur_comm_rung))) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Nature frequency", y = "Flourishing (fm)", color = "High Macarthur Community status") 
```

## Nature freq x Macarthur Community -> Satisfaction with life  
```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%  
  lm(swl ~ nature_freq * macarthur_comm_rung, .) %>%
  summary
df_proc %>%
  ggplot(aes(x = nature_freq, y = swl, 
             color = factor(high_macarthur_comm_rung))) + 
  geom_point(alpha = .3) +
  geom_smooth(method = "lm") +
  labs(x = "Nature frequency", y = "Satisfaction with life (swl)", color = "High Macarthur Community status")
```

## ** Nature freq x Macarthur Community -> Negative affect  

* Higher community status = more negative affect with nature contact?

```{r, message=F}
df_proc %>% 
  dplyr::mutate_if(is.numeric, scale) %>%   
  lm(panas_neg ~ nature_freq * macarthur_comm_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_freq, y = panas_neg, 
             color = factor(high_macarthur_comm_rung))) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Nature frequency", y = "Negative affect (PANAS-neg)", color = "High Macarthur Community status") 
```

## ** Nature freq x Macarthur Community -> Perceived stress 

* Higher community status = more stress with nature contact?

```{r, message=F}
df_proc %>%
  dplyr::mutate_if(is.numeric, scale) %>%   
  lm(pss ~ nature_freq * macarthur_comm_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_freq, y = pss,
             color = factor(high_macarthur_comm_rung))) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Nature frequency", y = "Perceived stress (pss)", color = "High Macarthur Community status") 
```



# H2b: Moderations mediated by reappraisal and rumination 

```{r}
run_mediated_moderation <- function(a1, a2, b, c, ...){
  mod <- glue('
{b} ~ a*{a1}:{a2} + {a1} + {a2}
{c} ~ b*{b} + cp*{a1}:{a2} + {a1} + {a2}
indirect := a*b
total := indirect + cp
')
  fit <- sem(mod, ...)
  
  parameterEstimates(
    fit,
    boot.ci.type="bca.simple",
    level=0.95,
    ci=TRUE,
    standardized = TRUE
  ) %>% 
    as.data.frame %>% 
    dplyr::mutate_if(is.numeric, ~round(., 3)) %>% 
    select(-std.lv, -std.nox) %>% 
    knitr::kable() %>% 
    print
  
  return(fit)
}

```


We hypothesize that these moderations will be mediated by frequency of reappraisal and rumination.

## Nature time x ACE -> Reappraisal -> Pos affect 

* Non-significant indirect effect 
```{r, message=F}
fit <- run_mediated_moderation("nature_time", "high_ace",
                               "pmerq_reappraise", 
                               "panas_pos",
                               se="bootstrap",
                               data=df_proc)

```

## Nature time x ACE -> Rumination -> Pos affect 

* Non-significant indirect effect
```{r, message=F}
fit <- run_mediated_moderation("nature_time", "high_ace",
                               "rrs_brood", 
                               "panas_pos",
                               se="bootstrap",
                               data=df_proc)
```

## Nature time x ACE -> Reappraisal -> Neg affect 

* Non-significant indirect effect
```{r, message=F}
fit <- run_mediated_moderation("nature_time", "high_ace",
                               "pmerq_reappraise", 
                               "panas_neg",
                               se="bootstrap",
                               data=df_proc)
```

## Nature time x ACE -> Rumination -> Neg affect

* Non-significant indirect effect
```{r, message=F}
fit <- run_mediated_moderation("nature_time", "high_ace",
                               "rrs_brood", 
                               "panas_neg",
                               se="bootstrap",
                               data=df_proc)
```

## Nature time x Macarthur US -> Reappraisal -> SWL

* Non-significant indirect effect 
```{r, message=F}
fit <- run_mediated_moderation("nature_time", "macarthur_us_rung",
                               "pmerq_reappraise", 
                               "swl",
                               se="bootstrap",
                               data=df_proc)
```

## Nature time x Macarthur US -> Rumination -> SWL

* Non-significant indirect effect 
```{r, message=F}
fit <- run_mediated_moderation("nature_time", "macarthur_us_rung",
                               "rrs_brood", 
                               "swl",
                               se="bootstrap",
                               data=df_proc)
```

## Nature freq x ACE -> Reappraisal -> Flourishing

* Non-significant indirect effect 

```{r, message=F}
fit <- run_mediated_moderation("nature_freq", "high_ace",
                               "pmerq_reappraise", 
                               "fm",
                               se="bootstrap",
                               data=df_proc)
```

## Nature freq x ACE -> Rumination -> Flourishing

* Non-significant indirect effect 

```{r, message=F}
fit <- run_mediated_moderation("nature_freq", "high_ace",
                               "rrs_brood", 
                               "fm",
                               se="bootstrap",
                               data=df_proc)
```

## Nature freq x ACE -> Reappraisal -> SWL

* Non-significant indirect effect 

```{r, message=F}
fit <- run_mediated_moderation("nature_freq", "high_ace",
                               "pmerq_reappraise", 
                               "swl",
                               se="bootstrap",
                               data=df_proc)
```

## Nature freq x ACE -> Rumination -> SWL

* Non-significant indirect effect 

```{r, message=F}
fit <- run_mediated_moderation("nature_freq", "high_ace",
                               "rrs_brood", 
                               "swl",
                               se="bootstrap",
                               data=df_proc)
```

## Nature freq x Macarthur US -> Reappraisal -> Neg affect

* Non-significant indirect effect 

```{r, message=F}
fit <- run_mediated_moderation("nature_freq", "macarthur_us_rung",
                               "pmerq_reappraise", 
                               "panas_neg",
                               se="bootstrap",
                               data=df_proc)
```

## Nature freq x Macarthur US -> Rumination -> Neg affect

* Non-significant indirect effect 

```{r, message=F}
fit <- run_mediated_moderation("nature_freq", "macarthur_us_rung",
                               "rrs_brood", 
                               "panas_neg",
                               se="bootstrap",
                               data=df_proc)
```

## Nature freq x Macarthur US -> Reappraisal -> Perceived stress

* Non-significant indirect effect 

```{r, message=F}
fit <- run_mediated_moderation("nature_freq", "macarthur_us_rung",
                               "pmerq_reappraise", 
                               "pss",
                               se="bootstrap",
                               data=df_proc)
```

## ** Nature freq x Macarthur US -> Rumination -> Perceived stress

* Non-significant indirect effect 

```{r, message=F}
fit <- run_mediated_moderation("nature_freq", "macarthur_us_rung",
                               "rrs_brood", 
                               "pss",
                               se="bootstrap",
                               data=df_proc)
```

## Nature freq x Macarthur community -> Reappraisal -> Neg affect

* Non-significant indirect effect 

```{r, message=F}
fit <- run_mediated_moderation("nature_freq", "macarthur_comm_rung",
                               "pmerq_reappraise", 
                               "panas_neg",
                               se="bootstrap",
                               data=df_proc)
```

## *** Nature freq x Macarthur community -> Rumination -> Neg affect

```{r, message=F}
fit <- run_mediated_moderation("nature_freq", "macarthur_comm_rung",
                               "rrs_brood", 
                               "panas_neg",
                               se="bootstrap",
                               data=df_proc)
```

## Nature freq x Macarthur community -> Reappraisal -> Perceived stress

* Non-significant indirect effect 

```{r, message=F}
fit <- run_mediated_moderation("nature_freq", "macarthur_comm_rung",
                               "pmerq_reappraise", 
                               "pss",
                               se="bootstrap",
                               data=df_proc)
```

## *** Nature freq x Macarthur community -> Rumination -> Perceived stress


```{r, message=F}
fit <- run_mediated_moderation("nature_freq", "macarthur_comm_rung",
                               "rrs_brood", 
                               "pss",
                               se="bootstrap",
                               data=df_proc)
```


# Session Info
```{r, message=F}
sessionInfo()
```

