---
title: "Nature ER National Qualtrics Study"
author: "Ashish and Jordan"
date: "2021-05-24"
output: rmdformats::readthedown
---

# Notes
## TODO 
* Need to figure out how to deal with heteroscedasticity for time in nature. E.g. in mediation models
  * Lim & Melville. (2009). Robustness of Structural Equation Modeling to Distributional Misspecification: Empirical Evidence & Research Guidelines 
* Mediated moderation

# Initialization
```{r, message=FALSE}
rm(list=ls())
library(lavaan)
library(lmerTest)
library(here)
library(tidyverse)
library(tidylog)
require(rmdformats)
theme_set(theme_bw())
```

# Preprocessing 
## Functions 
```{r, message=F, warning=F}
codebook_renamer <- function(df, codebook, old_col_name="old_col_name", new_col_name="new_col_name"){
  codebook <- codebook %>%
    dplyr::filter(.data[[old_col_name]] %in% names(df))
  df %>% 
  rename_at(vars(codebook[[old_col_name]]), ~codebook[[new_col_name]])
}

codebook_recoder <- function(df,
                             codebook,
                             var_col_name="var_regex",
                             old_value_col="old_value",
                             new_value_col="new_value",
                             to_numeric=TRUE){
  require(dplyr)
  var_regexes <- unique(codebook[[var_col_name]])
  recode_column <- function(column, level_key){dplyr::recode(tolower(column), !!!level_key)}
  for(var in var_regexes){
    level_key <- codebook %>% 
      # --  remove line breaks -- #
      dplyr::mutate_at(vars(one_of(old_value_col)), ~str_replace_all(., "\\\r|\\\n", "")) %>%
      dplyr::filter(.data[[var_col_name]]==!!var) %>% 
      dplyr::mutate("{old_value_col}" := tolower(.data[[old_value_col]])) %>% 
      dplyr::select(one_of(old_value_col, new_value_col)) %>%
      deframe
    df <- df %>% 
      dplyr::mutate_at(vars(matches(paste0("^", var))), ~str_replace_all(., "\\\r|\\\n", "")) %>% 
      dplyr::mutate_at(vars(matches(paste0("^", var))), ~recode_column(., level_key))
    if(to_numeric){df <- df %>% dplyr::mutate_at(vars(matches(paste0("^", var))), as.numeric)}
  }
  return(df)
}
tally_scale <- function(df, 
                        scale_regex, 
                        new_col_name=NULL, 
                        pid_col="pid", 
                        join_function=dplyr::full_join, 
                        na.rm=F, 
                        tally_function=sum){
  # if user did not supply a new column name, use the scale_regex
  if(is.null(new_col_name)) new_col_name <- scale_regex 
  # check is there are duplicate participant IDs
  if(any(duplicated(df[[pid_col]]))){stop("Duplicate IDs found")}
  # append caret to start of regex
  scale_regex <- paste0("^", scale_regex) 
  # identify columns to tally
  cols_to_tally <- names(df)[str_detect(names(df), scale_regex)] 
  print(paste0("[",new_col_name, "] tallying columns:"))
  print(cols_to_tally)
  df_tally <- df %>% 
    dplyr::select(one_of(pid_col), one_of(cols_to_tally)) %>% # select columns to aggregate
    tidyr::pivot_longer(-one_of(pid_col)) %>% # convert to long format 
    dplyr::group_by_at(pid_col) %>% # group by participant
    dplyr::mutate(value = as.numeric(value)) %>% # change values to numeric
    dplyr::summarize(!!new_col_name := tally_function(value, na.rm=na.rm)) # aggregate according to tally_function
  if(!is.null(join_function)){
    df_tally <- df %>%
      join_function(df_tally) # join aggregated scores with original dataframe using join_function
  }
  return(df_tally)
}

```

## Read data
```{r, message=F}
codebook_filepath <- here("lib/Winter_2020_Survey_EWB_S2B_National_April_26_2021_11_30_codebook.xlsx")
codebook_vars <- readxl::read_excel(codebook_filepath, sheet="variables")
codebook_values <- readxl::read_excel(codebook_filepath, sheet="values") %>% 
  mutate(old_value = str_replace_all(old_value, "\r", ""))

df_file <- readxl::read_excel(here("data/raw/2021-06-03/national_study_2b_raw.xlsx")) %>% 
  filter_all(any_vars(!is.na(.)))
df_raw <- df_file %>% 
  slice(-1:-2) %>% 
  # -- rename columns -- #
  codebook_renamer(codebook=codebook_vars)


```

## Constants
```{r, message=F}
columns_to_numeric <- c("nature_time", "age", "perceived_exertion")
```

## Functions
```{r}
get_race <- function(df, race_column="race"){
  # Function to turn race column into several columns with binary values
  tibble(
    white = str_detect(df[[race_column]], "White"),
    black = str_detect(df[[race_column]], "Black"),
    amindian = str_detect(df[[race_column]], "American Indian"),
    eastasian = str_detect(df[[race_column]], "East Asian"),
    filipino = str_detect(df[[race_column]], "Filipin"),
    seasian = str_detect(df[[race_column]], "Southeast Asian"),
    otherasian = str_detect(df[[race_column]], "Other Asian"),
    pacisland = str_detect(df[[race_column]], "Pacific"),
    chicano = str_detect(df[[race_column]], "Chican"),
    puertorican = str_detect(df[[race_column]], "Puerto"),
    centralamerican = str_detect(df[[race_column]], "Central American"),
    southamerican = str_detect(df[[race_column]], "South American"),
    otherlatin = str_detect(df[[race_column]], "Other Hispanic"),
    other = str_detect(df[[race_column]], "Other(?! Hispanic)(?! Asian)"),
    prefernot = str_detect(df[[race_column]], "Prefer not")
  ) %>% 
    rename_all(~paste0("race_", .)) %>% 
    mutate_all(as.integer)
}

```


## Process data

```{r, message=F}
df_recoded <- df_raw %>%
	# -- recode variables -- #
	codebook_recoder(codebook=codebook_values) %>% 
  mutate(perceived_exertion = str_extract(perceived_exertion, "^[0-9]*"))

df_proc <- df_recoded %>%
  
  # -- remove failed attention checks -- #
  filter(ac_1 == 1 & ac_2 == 1 & ac_3 == 1) %>% 
  
  # -- create pids -- #
  mutate(pid = seq(from = 1000, length.out = n())) %>%

  # -- revalue invalid age, e.g. age = 2000 becomes age = 21 -- #
  mutate(age = as.numeric(age))%>%
  mutate(age = ifelse(age > 1000, 2021-age, age)) %>%
  
  # -- assign NA to people who don't report income -- #
  mutate(income = ifelse(income == "Prefer not to say", NA, income)) %>%

  # -- create log transformed nature time -- #
  mutate(nature_time = as.numeric(nature_time)) %>%
  mutate(nature_time_log = ifelse(nature_time == 0, nature_time, log(nature_time))) %>%
  
  # -- tally scales -- # 
  tally_scale("paq.*[0-9]{1,2}$", "paq") %>% 
  tally_scale("paq_.*_dif_[0-9]{1,2}$", "paq_dif") %>% 
  tally_scale("paq_.*_ddf_[0-9]{1,2}$", "paq_ddf") %>% 
  tally_scale("paq_.*_eot_[0-9]{1,2}$", "paq_eot") %>% 
  tally_scale("paq_pos_.*_[0-9]{1,2}$", "paq_pos") %>% 
  tally_scale("paq_neg_.*_[0-9]{1,2}$", "paq_neg") %>% 
  tally_scale("paq_neg_dif_[0-9]{1,2}$", "paq_neg_dif") %>% 
  tally_scale("paq_neg_ddf_[0-9]{1,2}$", "paq_neg_ddf") %>% 
  tally_scale("paq_pos_dif_[0-9]{1,2}$", "paq_pos_dif") %>% 
  tally_scale("paq_pos_ddf_[0-9]{1,2}$", "paq_pos_ddf") %>% 
  
  tally_scale("pmerq_(recons|repurp)_.*_[0-9]{1,2}$", "pmerq_reappraise") %>% 
  tally_scale("pmerq_attdep_.*_[0-9]{1,2}$", "pmerq_attdep") %>% 
  
  tally_scale("sitselect_(approach|avoid)_[1-6]$", "sitselect") %>% 
  tally_scale("sitselect_approach_[1-6]$", "sitselect_approach") %>% 
  tally_scale("sitselect_avoid_[1-6]$", "sitselect_avoid") %>% 
  tally_scale("pmerq_sitsel_dis_[0-9]{1,2}$", "pmerq_sitsel_dis") %>%
  tally_scale("pmerq_sitsel_eng_[0-9]{1,2}$", "pmerq_sitsel_eng") %>%
  tally_scale("pmerq_sitmod_eng_[0-9]{1,2}$", "pmerq_sitmod_eng") %>%
  tally_scale("pmerq_sitmod_dis_[0-9]{1,2}$", "pmerq_sitmod_dis") %>%
  tally_scale("pmerq_attdep_eng_[0-9]{1,2}$", "pmerq_attdep_eng") %>%
  tally_scale("pmerq_attdep_dis_[0-9]{1,2}$", "pmerq_attdep_dis") %>%
  tally_scale("pmerq_recons_eng_[0-9]{1,2}$", "pmerq_recons_eng") %>%
  tally_scale("pmerq_recons_dis_[0-9]{1,2}$", "pmerq_recons_dis") %>%
  tally_scale("pmerq_recons_(dis|eng)_[0-9]{1,2}$", "pmerq_recons") %>%
  tally_scale("pmerq_repurp_eng_[0-9]{1,2}$", "pmerq_repurp_eng") %>%
  tally_scale("pmerq_repurp_dis_[0-9]{1,2}$", "pmerq_repurp_dis") %>%
  tally_scale("pmerq_repurp_(eng|dis)_[0-9]{1,2}$", "pmerq_repurp") %>%
  tally_scale("pmerq_respmod_dis_[0-9]{1,2}$", "pmerq_respmod_dis") %>%
  tally_scale("pmerq_respmod_eng_[0-9]{1,2}$", "pmerq_respmod_eng") %>%

  tally_scale("fm_[0-9]{1,2}$", "fm") %>%
  tally_scale("swl_[1-5]$", "swl") %>%
  tally_scale("pss_", "pss") %>%
  tally_scale("fcv_[1-7]$", "fcv") %>%
  tally_scale("sds_", "sds") %>%

  tally_scale("panas_pos_[0-9]{1,2}$", "panas_pos") %>%
  tally_scale("panas_neg_[0-9]{1,2}$", "panas_neg") %>%

  tally_scale("rrs_brood_[0-9]$", "rrs_brood") %>%
  
  tally_scale("tas_", "tas") %>%
  tally_scale("tas_dif_[0-9]{1,2}$", "tas_dif") %>%
  tally_scale("tas_ddf_[0-9]{1,2}$", "tas_ddf") %>%
  tally_scale("tas_eot_[0-9]{1,2}$", "tas_eot") %>%
  
  tally_scale("ace_[0-9]$", "ace") %>% 
  
  # -- data types -- #
  mutate_at(vars(one_of(columns_to_numeric)), as.numeric) %>% 
  # -- re-order factors -- #
  mutate(edu = factor(edu, levels = c( 
    "Less than high school degree",
    "High school graduate (high school diploma or equivalent including GED)",
    "Some college but no degree",
    "Associate degree in college (2-year)",
    "Bachelor's degree in college (4-year)",
    "Master's degree",
    "Professional degree (JD, MD)",
    "Doctoral degree"
  ))) %>% 
  
  mutate(income = factor(income, levels = c(
    "Less than $10,000",
    "$10,000 to $19,999",
    "$20,000 to $29,999",
    "$30,000 to $39,999",
    "$40,000 to $49,999",
    "$50,000 to $59,999",
    "$60,000 to $69,999",
    "$70,000 to $79,999",
    "$80,000 to $89,999",
    "$90,000 to $99,999",
    "$100,000 to $149,999",
    "$150,000 to $199,999",
    "$200,000 to $249,999",
    "$250,000 to $299,999",
    "$300,000 or more"
  ))) %>%
  
  mutate(nature_freq = factor(nature_freq, levels = c(
  "Never",
  "Once a year",
  "Once every three months",
  "Once a month",
  "2-3 times a month",
  "Once a week",
  "2-3 days a week",
  "3-5 days a week",
  "6-7 days a week"
  ))) %>%
  
  # -- discretizing continuous variables for visualizations -- #
  mutate(high_ace = case_when(
    ace <= 4 ~ 0, 
    ace > 4 ~ 1)) %>% 
  mutate(high_macarthur_us_rung = case_when(
    macarthur_us_rung <= median(macarthur_us_rung) ~ 0,
    macarthur_us_rung > median(macarthur_us_rung) ~ 1)) %>% 
  mutate(high_macarthur_comm_rung = case_when(
    macarthur_comm_rung <= median(macarthur_comm_rung) ~ 0,
    macarthur_comm_rung > median(macarthur_comm_rung) ~ 1)) %>% 
  cbind(get_race(.))
```



```{r, echo=FALSE}
# ------ End Preprocessing ------ #
# ----- Run all chunks above -----#
```

# Preregistration 
## Hypotheses

[Pre-registration](https://osf.io/t94h2) 

1A. We hypothesize that nature contact will be associated with greater frequency of (i) situation selection in the form of approaching positively valenced situations, (ii) distraction, and (iii) reappraisal strategies and (iv) lesser frequency of rumination. Moreover, we hypothesize that emotion regulation strategies will be related to affective outcomes.

1B. We hypothesize that frequency of distraction, reappraisal, and rumination will mediate the association of nature contact with affective outcomes.

2A. We hypothesize that nature contact will moderate the associations of (i) adverse life experiences and (ii) perceived social status with affective outcomes.

2B. We hypothesize that these moderations will be mediated by frequency of reappraisal and rumination.

## Statistical analysis 

Multiple regression models will test whether time with nature predicts positive affect, negative affect, and emotion regulation (reappraisal, rumination, suppression); and whether situation selection predicts time with nature; controlling for fear of COVID-19, Nature Relatedness, and age/demographic covariates. We will use model comparison procedures (i.e. LR-test and AIC/BIC) to determine whether covariates improve model fit and include them in the final model contingent on this procedure. Multiple regression analysis will also allow for us to test whether the relationship between ACE scores and perceived social status with affect is moderated by time with nature.

Structural equation modeling will be used to test whether emotion regulation mediates the association of time with nature with affective outcomes. We will evaluate bootstrapped confidence intervals for indirect effects to determine significance of mediation.

## Data exclusion

Participants must pass 4/4 attention checks to be included.

Following Leiner (2019), we will remove participants based on implausible completion times using the following procedure: "For each page, the sample’s median page completion time is divided by the individual completion time, resulting in a speed factor. A factor of 2 means that the respondent has completed a page twice as fast as the typical respondent. An average speed factor per respondent is computed after the page factors are clipped to a maximum value of 3."
We will exclude participants who respond with an average speed factor greater than 2.

Sensitivity analyses will be run to compare results with and without outliers.

# Distributions 

##  Total N
```{r, message=F}
df_proc %>% 
  nrow
df_proc %>% 
  pull(pid) %>% 
  unique %>% 
  length
```

## Demographics

### Gender
```{r, message=F}
df_proc %>% 
  group_by(gender) %>% 
  summarize(n = n())
```

### Age
```{r, message=F}
df_proc %>% 
  ggplot(aes(x = age)) + 
  geom_histogram(binwidth = 10) + 
  labs(x = "Age", y = "count") + 
  ggtitle("Age histogram")

# Get mean age and standard deviation
df_proc %>% 
  summarize(mean_age = mean(age, na.rm = T),
            sd_age = sd(age, na.rm = T))

```


### MacArthur status
```{r, message=F}
# MacArthur US histogram
df_proc %>%
  ggplot(aes(x=macarthur_us_rung))+
  geom_histogram(binwidth = 1) +
  labs(x = "MacArthur Rung US", y = "count") +
  ggtitle("MacArthur Rung US histogram")

# MacArthur community histogram
df_proc %>%
  ggplot(aes(x=macarthur_comm_rung))+
  geom_histogram(binwidth = 1) +
  labs(x = "MacArthur Rung Community", y = "count") +
  ggtitle("MacArthur Rung Community histogram")
```

### Education
```{r, message=F}
df_proc %>% 
  ggplot(aes(x = edu)) + 
  geom_bar() +
  labs(x = "Education", y = "count") +
  coord_flip() # rotate the plot
```

### Income
```{r, message=F}
df_proc %>%
  ggplot(aes(x = income)) + 
  geom_bar() + 
  labs(x = "Income", y = "count") +
  coord_flip()
```

### Race

```{r, message=F}
df_race <- df_proc %>% 
  select(pid, starts_with("race_")) %>% 
  select(-race_text) %>% 
  pivot_longer(!pid, names_to = "race") %>% 
  group_by(race) %>% 
  summarize(n = sum(value),
            pr = mean(value)) %>% 
  mutate(race = str_replace(race, "race_", "")) %>% 
  arrange(n) %>% 
  mutate(race = fct_reorder(race, n))
    
df_race %>% 
  knitr::kable()
df_race %>% 
  ggplot(aes(x = race, y = n)) +
  geom_bar(stat="identity") +
  coord_flip()
  
```

## Time in nature 
> Over the last month, approximately how many HOURS PER WEEK do you consider yourself to have interacted with nature? This includes, for example, walking, biking, or recreating outside in local, regional, or national parks, at the beach, beside or within lakes, creeks, or the ocean, gardening or tending to plants, camping, fishing, reading or walking outside next to trees, engaging in yard work with natural elements, etc...

* Highly skewed distribution

```{r, message=F}

df_proc %>% 
  ggplot(aes(x = nature_time)) + 
  geom_histogram(binwidth = 5) + 
  labs(x = "hours/week in nature", y = "count") + 
  ggtitle("Hours/week in nature histogram")

df_proc %>% 
  ggplot(aes(x = nature_time_log)) + 
  geom_histogram(binwidth = 0.5) +
  labs(x = "log transformed hours/week in nature", y = "count") + 
  ggtitle("Log-transformed hours/week in nature histogram")
```

## Frequency of nature contact
> About how often do you usually visit or pass through outdoor natural areas for any reason? This includes, for example, walking, biking, or recreating outside in local, regional, or national parks, at the beach, beside or within lakes, creeks, or the ocean, gardening or tending to plants, camping, fishing, reading or walking outside next to trees, engaging in yard work with natural elements, etc...

```{r, message=F}
df_proc %>%
  ggplot(aes(x = nature_freq)) + 
  geom_bar() +
  labs(x = "frequency of nature contact", y = "count") +
  ggtitle("Frequency of nature contact histogram") +
  coord_flip()
```

## Nature setting
> Which option best describes where, in the past month, most of your nature exposure took place? If you spent time in multiple nature areas, please pick the option where you spent the most time. 

```{r, message=F}
df_proc %>%
  ggplot(aes(x = nature_setting)) +
  geom_bar() +
  labs(x = "nature setting", y = "count") +
  ggtitle("Nature setting histogram") +
  coord_flip()
```

## Perceived exertion in nature
> Please rate your perception of exertion, i.e. how heavy and strenuous the exercise felt to you and how tired you were, when you were in the natural area during which you spent the most time in the past month. The perception of exertion is mainly felt as strain and fatigue in your muscles and as breathlessness or aches in the chest. Use this scale from 6 to 20, where 6 means “No exertion at all” and 20
means “Maximal exertion.”

```{r, message=F}
df_proc %>%
  ggplot(aes(x = perceived_exertion)) +
  geom_histogram(binwidth = 1) +
  labs(x = "perceived exertion", y = "count") +
  ggtitle("Perceived exertion in nature histogram")
```



## Situation selection frequency 

Vars: 
* sitselect 
* sitselect_approach
* sitselect_avoid 
* pmerq_sitsel_eng 
* pmerq_sitsel_dis 
```{r, message=F}

df_proc %>%
  ggplot(aes(x = sitselect)) +
  geom_histogram(binwidth = 1) +
  labs(x = "situation selection", y = "count") +
  ggtitle("Situation selection histogram")

df_proc %>%
  ggplot(aes(x = sitselect_approach)) +
  geom_histogram(binwidth = 1) +
  labs(x = "situation selection approach", y = "count") +
  ggtitle("Situation selection approach histogram")

  df_proc %>%
  ggplot(aes(x = sitselect_avoid)) +
  geom_histogram(binwidth = 1) +
  labs(x = "situation selection avoid", y = "count") +
  ggtitle("Situation selection avoid histogram")

df_proc %>%
  ggplot(aes(x = pmerq_sitsel_eng)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ situation selection engagement", y = "count") +
  ggtitle("PMERQ situation selection engagement histogram")

df_proc %>%
  ggplot(aes(x = pmerq_sitsel_dis)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ situation selection disengagement", y = "count") +
  ggtitle("PMERQ situation selection disengagement histogram")
```

## Situation modification frequency

Vars: 
* pmerq_sitmod_eng 
* pmerq_sitmod_dis 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = pmerq_sitmod_eng)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ situation modification engagement", y = "count") +
  ggtitle("PMERQ situation modification engagement histogram")

df_proc %>%
  ggplot(aes(x = pmerq_sitmod_dis)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ situation modification disengagement", y = "count") +
  ggtitle("PMERQ situation modification disengagement histogram")
```

## Distraction frequency

Vars: 
* pmerq_attdep 
* pmerq_attdep_eng 
* pmerq_attdep_dis 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = pmerq_attdep)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ attention deployment", y = "count") +
  ggtitle("PMERQ attention deployment histogram")

df_proc %>%
  ggplot(aes(x = pmerq_attdep_eng)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ attention deployment engagement", y = "count") +
  ggtitle("PMERQ attention deployment engagement histogram")

df_proc %>%
  ggplot(aes(x = pmerq_attdep_dis)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ attention deployment disengagement", y = "count") +
  ggtitle("PMERQ attention deployment disengagement histogram")
```

## Rumination frequency 

Vars: 
* rrs_brood 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = rrs_brood)) +
  geom_histogram(binwidth = 1) +
  labs(x = "ruminative response brooding", y = "count") +
  ggtitle("Brooding (Rumination Reponse Scale) histogram")
```

## Reappraisal frequency 

Vars:
* pmerq_reappraise 
* pmerq_recons 
* pmerq_recons_eng
* pmerq_recons_dis
* pmerq_repurp 
* pmerq_repurp_eng  
* pmerq_repurp_dis 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = pmerq_reappraise)) +
  geom_histogram(binwidth = 5) +
  labs(x = "PMERQ reappraisal", y = "count") +
  ggtitle("PMERQ reappraisal histogram")

df_proc %>%
  ggplot(aes(x = pmerq_recons)) +
  geom_histogram(binwidth = 2) +
  labs(x = "PMERQ reconstrual", y = "count") +
  ggtitle("PMERQ reconstrual histogram")

df_proc %>%
  ggplot(aes(x = pmerq_recons_eng)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ reconstrual engagement", y = "count") +
  ggtitle("PMERQ reconstrual engagement histogram")

df_proc %>%
  ggplot(aes(x = pmerq_recons_dis)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ reconstrual disengagement", y = "count") +
  ggtitle("PMERQ reconstrual disengagement histogram")

df_proc %>%
  ggplot(aes(x = pmerq_repurp)) +
  geom_histogram(binwidth = 2) +
  labs(x = "PMERQ repurposing", y = "count") +
  ggtitle("PMERQ repurposing histogram")

df_proc %>%
  ggplot(aes(x = pmerq_repurp_eng)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ repurposing engagement", y = "count") +
  ggtitle("PMERQ repurposing engagement histogram")

df_proc %>%
  ggplot(aes(x = pmerq_repurp_dis)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ repurposing disengagement", y = "count") +
  ggtitle("PMERQ repurposing disengagement histogram")
```

## Suppression frequency 

Vars:
* pmerq_respmod_dis 

```{r, message=F}
df_proc %>%
  ggplot(aes(x = pmerq_respmod_dis)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ response modulation disengagement", y = "count") +
  ggtitle("Suppression frequency histogram")
```

## Social support frequency 

Vars:
* pmerq_respmod_eng  
```{r, message=F}
df_proc %>%
  ggplot(aes(x = pmerq_respmod_eng)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PMERQ response modulation engagement", y = "count") +
  ggtitle("Social support histogram")
```


## Flourishing 

Vars:
* fm
```{r, message=F}
df_proc %>%
  ggplot(aes(x = fm)) +
  geom_histogram(binwidth = 5) +
  labs(x = "flourishing measure score", y = "count") +
  ggtitle("Flourishing histogram")
```

## Satisfaction with life 

Vars:
* swl 
```{r, message=F}

df_proc %>%
  ggplot(aes(x = swl)) +
  geom_histogram(binwidth = 1) +
  labs(x = "satisfaction with life score", y = "count") +
  ggtitle("Satisfaction with life histogram")
```

## Positive affect (PANAS)

Vars: 
* panas_pos 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = panas_pos)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PANAS positive affect score", y = "count") +
  ggtitle("PANAS positive affect histogram")
```

## Negative affect (PANAS) 

Vars: 
* panas_neg 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = panas_neg)) +
  geom_histogram(binwidth = 1) +
  labs(x = "PANAS negative affect score", y = "count") +
  ggtitle("PANAS negative affect histogram")
```

## Perceived Stress 

Vars:
* pss 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = pss)) +
  geom_histogram(binwidth = 1) +
  labs(x = "Perceived Stress Scale score", y = "count") +
  ggtitle("Perceived stress histogram")
```


## Alexithymia PAQ 

Vars: 
* paq 
* paq_dif 
* paq_ddf 
* paq_eot 
* paq_pos 
* paq_neg 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = paq)) +
  geom_histogram(binwidth = 5) +
  labs(x = "PAQ score", y = "count") +
  ggtitle("PAQ histogram")

df_proc %>%
  ggplot(aes(x = paq_dif)) +
  geom_histogram(binwidth = 3) +
  labs(x = "PAQ difficulty identifying feelings score", y = "count") +
  ggtitle("PAQ difficulty identifying feelings histogram")

df_proc %>%
  ggplot(aes(x = paq_ddf)) +
  geom_histogram(binwidth = 3) +
  labs(x = "PAQ difficulty describing feelings score", y = "count") +
  ggtitle("PAQ difficulty describing feelings histogram")

df_proc %>%
  ggplot(aes(x = paq_eot)) +
  geom_histogram(binwidth = 3) +
  labs(x = "PAQ externally oriented thinking score", y = "count") +
  ggtitle("PAQ externally oriented thinking histogram")

df_proc %>%
  ggplot(aes(x = paq_pos)) +
  geom_histogram(binwidth = 3) +
  labs(x = "PAQ positive score", y = "count") +
  ggtitle("PAQ positive histogram")

df_proc %>%
  ggplot(aes(x = paq_neg)) +
  geom_histogram(binwidth = 3) +
  labs(x = "PAQ negative score", y = "count") +
  ggtitle("PAQ negative histogram")
```

## Alexithymia TAS 

Vars: 
* tas 
* tas_dif 
* tas_ddf 
* tas_eot
```{r, message=F}
df_proc %>%
  ggplot(aes(x = tas)) +
  geom_histogram(binwidth = 2) +
  labs(x = "TAS total score", y = "count") +
  ggtitle("TAS total score histogram")

df_proc %>%
  ggplot(aes(x = tas_dif)) +
  geom_histogram(binwidth = 1) +
  labs(x = "TAS difficulty identifying feelings score", y = "count") +
  ggtitle("TAS difficulty identifying feelings histogram")

df_proc %>%
  ggplot(aes(x = tas_ddf)) +
  geom_histogram(binwidth = 1) +
  labs(x = "TAS difficulty describing feelings score", y = "count") +
  ggtitle("TAS difficulty describing feelings histogram")

df_proc %>%
  ggplot(aes(x = tas_eot)) +
  geom_histogram(binwidth = 1) +
  labs(x = "TAS externally oriented thinking score", y = "count") +
  ggtitle("TAS externally oriented thinking histogram")
```


## Fear of coronavirus 

Vars: 
* fcv 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = fcv)) +
  geom_histogram(binwidth = 1) +
  labs(x = "fear of coronavirus scale score", y = "count") +
  ggtitle("Fear of coronavirus histogram")
```

## Social desiribility 

Vars: 
* sds 
```{r, message=F}
df_proc %>%
  ggplot(aes(x = sds)) +
  geom_histogram(binwidth = 1) +
  labs(x = "social desiribility scale score", y = "count") +
  ggtitle("Social desiribility histogram")
```


# Confirmatory analyses

In these headings of these Confirmatory analyses, asteriks indicate significance of a hypothesized effect. 
† => p < .10 
* => p < .05 
** => p < .01 
*** => p < .001

# H1a: Nature contact and ER frequency 
We hypothesize that nature contact will be associated with greater frequency of (i) situation selection in the form of approaching positively valenced situations, (ii) distraction, and (iii) reappraisal strategies and (iv) lesser frequency of rumination. Moreover, we hypothesize that emotion regulation strategies will be related to affective outcomes. 

## * Nature time <-> situation selection approach pos
Results 
* r = .09, p = .030
* Heteroscedasticity 
```{r, message=F}
cor.test(df_proc$nature_time, df_proc$sitselect_approach)

df_proc %>% 
  ggplot(aes(x = sitselect_approach, y = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```


## Nature time <-> distraction 
```{r, message=F}
cor.test(df_proc$nature_time, df_proc$pmerq_attdep_dis)

df_proc %>% 
  ggplot(aes(x = pmerq_attdep_dis, y = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## ** Nature time <-> reappraisal 
```{r, message=F}
cor.test(df_proc$nature_time, df_proc$pmerq_reappraise)

df_proc %>% 
  ggplot(aes(x = pmerq_reappraise, y = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## † Nature time <-> rumination 
```{r, message=F}
cor.test(df_proc$nature_time, df_proc$rrs_brood)

df_proc %>% 
  ggplot(aes(x = rrs_brood, y = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## ** Nature time <-> flourishing 
```{r, message=F}
cor.test(df_proc$nature_time, df_proc$fm)

df_proc %>% 
  ggplot(aes(x = fm, y = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## *** Nature time <-> satisfaction with life 
```{r, message=F}
cor.test(df_proc$nature_time, df_proc$swl)

df_proc %>% 
  ggplot(aes(y = swl, x = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## Nature time <-> perceived stress 
```{r, message=F}
cor.test(df_proc$nature_time, df_proc$pss)

df_proc %>% 
  ggplot(aes(x = pss, y = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## *** Nature time <-> positive affect 
```{r, message=F}
cor.test(df_proc$nature_time, df_proc$panas_pos)

df_proc %>% 
  ggplot(aes(x = panas_pos, y = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## Nature time <-> negative affect 
```{r, message=F}
cor.test(df_proc$nature_time, df_proc$panas_neg)

df_proc %>% 
  ggplot(aes(x = panas_neg, y = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```


# H1b: Nature exposure -> ER -> affect 
We hypothesize that frequency of distraction, reappraisal, and rumination will mediate the association of nature contact with affective outcomes.

## Nature time -> Rumination -> Positive affect 
* Non-significant indirect effect
```{r, message=F}
mod <- '
rrs_brood ~ a*nature_time
panas_pos ~ b*rrs_brood + cp*nature_time
indirect := a*b
total := indirect + cp
'
fit <- sem(mod, 
           se="bootstrap",
           data=df_proc)
summary(
  fit, 
  fit.measures=T, 
  rsq=T, 
  standardized=T
)

parameterEstimates(
  fit,
  boot.ci.type="bca.simple",
  level=0.95,
  ci=TRUE,
  standardized = TRUE
) %>% 
  as.data.frame %>% 
  mutate_if(is.numeric, ~round(., 3)) %>% 
  select(-std.lv, -std.nox)
```

## Nature time -> Distraction -> Positive affect 
* Non-significant indirect effect
```{r, message=F}
mod <- '
pmerq_attdep_dis ~ a*nature_time
panas_pos ~ b*pmerq_attdep_dis + cp*nature_time
indirect := a*b
total := indirect + cp
'
fit <- sem(mod, 
           se="bootstrap",
           data=df_proc)
summary(
  fit, 
  fit.measures=T, 
  rsq=T, 
  standardized=T
)

parameterEstimates(
  fit,
  boot.ci.type="bca.simple",
  level=0.95,
  ci=TRUE,
  standardized = TRUE
) %>% 
  as.data.frame %>% 
  mutate_if(is.numeric, ~round(., 3)) %>% 
  select(-std.lv, -std.nox)
```

## † Nature time -> Reappraisal -> Positive affect 
* indirect ß = -.009, p = .09
```{r, message=F}
mod <- '
pmerq_reappraise ~ a*nature_time
panas_pos ~ b*rrs_brood + cp*pmerq_reappraise
indirect := a*b
total := indirect + cp
'
fit <- sem(mod, 
           se="bootstrap",
           data=df_proc)
summary(
  fit, 
  fit.measures=T, 
  rsq=T, 
  standardized=T
)

parameterEstimates(
  fit,
  boot.ci.type="bca.simple",
  level=0.95,
  ci=TRUE,
  standardized = TRUE
) %>% 
  as.data.frame %>% 
  mutate_if(is.numeric, ~round(., 3)) %>% 
  select(-std.lv, -std.nox)
```

## Nature time -> Rumination -> Flourishing 
* Non-significant indirect effect 
```{r, message=F}
mod <- '
rrs_brood ~ a*nature_time
fm ~ b*rrs_brood + cp*nature_time
indirect := a*b
total := indirect + cp
'
fit <- sem(mod, 
           se="bootstrap",
           data=df_proc)
summary(
  fit, 
  fit.measures=T, 
  rsq=T, 
  standardized=T
)

parameterEstimates(
  fit,
  boot.ci.type="bca.simple",
  level=0.95,
  ci=TRUE,
  standardized = TRUE
) %>% 
  as.data.frame %>% 
  mutate_if(is.numeric, ~round(., 3)) %>% 
  select(-std.lv, -std.nox)
```

## Nature time -> Distraction -> Flourishing 
* Non-significant indirect effect 
```{r, message=F}
mod <- '
pmerq_attdep_dis ~ a*nature_time
fm ~ b*pmerq_attdep_dis + cp*nature_time
indirect := a*b
total := indirect + cp
'
fit <- sem(mod, 
           se="bootstrap",
           data=df_proc)
summary(
  fit, 
  fit.measures=T, 
  rsq=T, 
  standardized=T
)

parameterEstimates(
  fit,
  boot.ci.type="bca.simple",
  level=0.95,
  ci=TRUE,
  standardized = TRUE
) %>% 
  as.data.frame %>% 
  mutate_if(is.numeric, ~round(., 3)) %>% 
  select(-std.lv, -std.nox)
```

## Nature time -> Reappraisal -> Flourishing 
* indirect ß = .06, p = .008 
```{r, message=F}
mod <- '
pmerq_reappraise ~ a*nature_time
fm ~ b*pmerq_reappraise + cp*nature_time
indirect := a*b
total := indirect + cp
'
fit <- sem(mod, 
           se="bootstrap",
           data=df_proc)
summary(
  fit, 
  fit.measures=T, 
  rsq=T, 
  standardized=T
)

parameterEstimates(
  fit,
  boot.ci.type="bca.simple",
  level=0.95,
  ci=TRUE,
  standardized = TRUE
) %>% 
  as.data.frame %>% 
  mutate_if(is.numeric, ~round(., 3)) %>% 
  select(-std.lv, -std.nox)
```

## Nature time -> Rumination -> Satisfaction with life
* Non-significant indirect effect 
```{r, message=F}
mod <- '
rrs_brood ~ a*nature_time
swl ~ b*rrs_brood + cp*nature_time
indirect := a*b
total := indirect + cp
'
fit <- sem(mod,
           se="bootstrap",
           data=df_proc)
summary(
  fit,
  fit.measures=T,
  rsq=T,
  standardized=T
)

parameterEstimates(
  fit,
  boot.ci.type="bca.simple",
  level=0.95,
  ci=TRUE,
  standardized = TRUE
) %>%
  as.data.frame %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  select(-std.lv, -std.nox)
```

## Nature time -> Distraction -> Satisfaction with life 
* Non-significant indirect effect 
```{r, message=F}
mod <- '
pmerq_attdep_dis ~ a*nature_time
swl ~ b*pmerq_attdep_dis + cp*nature_time
indirect := a*b
total := indirect + cp
'
fit <- sem(mod,
           se="bootstrap",
           data=df_proc)
summary(
  fit,
  fit.measures=T,
  rsq=T,
  standardized=T
)

parameterEstimates(
  fit,
  boot.ci.type="bca.simple",
  level=0.95,
  ci=TRUE,
  standardized = TRUE
) %>%
  as.data.frame %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  select(-std.lv, -std.nox)
```

## ** Nature time -> Reappraisal -> Satisfaction with life 
* indirect effect ß = .05, p = .007
```{r, message=F}
mod <- '
pmerq_reappraise ~ a*nature_time
swl ~ b*pmerq_reappraise + cp*nature_time
indirect := a*b
total := indirect + cp
'
fit <- sem(mod,
           se="bootstrap",
           data=df_proc)
summary(
  fit,
  fit.measures=T,
  rsq=T,
  standardized=T
)

parameterEstimates(
  fit,
  boot.ci.type="bca.simple",
  level=0.95,
  ci=TRUE,
  standardized = TRUE
) %>%
  as.data.frame %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  select(-std.lv, -std.nox)
```

# H2a: Nature contact moderates association of adverse experience and affect 
We hypothesize that nature contact will moderate the associations of (i) adverse life experiences and (ii) perceived social status with affective outcomes. 

## † Nature time x adverse childhood experiences -> Positive affect 
* marginally significant when using binary ACE 
```{r, message=F}
df_proc %>% 
  lm(panas_pos ~ nature_time * ace, .) %>% 
  summary
df_proc %>% 
  lm(panas_pos ~ nature_time * high_ace, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = panas_pos, color = high_ace)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Positive affect (PANAS-pos)", color = "High ACE") 
```

## Nature time x adverse childhood experiences -> Flourishing 
```{r, message=F}
df_proc %>% 
  lm(fm ~ nature_time * ace, .) %>% 
  summary
df_proc %>% 
  lm(fm ~ nature_time * high_ace, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = fm, color = high_ace)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Flourishing (fm)", color = "High ACE") 
```

## Nature time x adverse childhood experiences -> Satisfaction with life  
```{r, message=F}

df_proc %>%
  lm(swl ~ nature_time * ace, .) %>%
  summary
df_proc %>%
  lm(swl ~ nature_time * high_ace, .) %>%
  summary
df_proc %>%
  ggplot(aes(x = nature_time, y = swl, color = high_ace)) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Satisfaction with life (swl)", color = "High ACE")
```

## † Nature time x adverse childhood experiences -> Negative affect 
* marginally significant when using binary ACE 
```{r, message=F}
df_proc %>% 
  lm(panas_neg ~ nature_time * ace, .) %>% 
  summary
df_proc %>% 
  lm(panas_neg ~ nature_time * high_ace, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = panas_neg, color = high_ace)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Negative affect (PANAS-neg)", color = "High ACE") 
```


## Nature time x adverse childhood experiences -> Perceived stress 
```{r, message=F}
df_proc %>% 
  lm(pss ~ nature_time * ace, .) %>% 
  summary
df_proc %>% 
  lm(pss ~ nature_time * high_ace, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = pss, color = high_ace)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Perceived stress (pss)", color = "High ACE") 
```

## Nature time x Macarthur US rung -> Positive affect
```{r, message=F}
df_proc %>% 
  lm(panas_pos ~ nature_time * macarthur_us_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = panas_pos, color = high_macarthur_us_rung)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Positive affect (PANAS-pos)", color = "High Macarthur US status") 
```

## Nature time x Macarthur US rung -> Flourishing 
```{r, message=F}
df_proc %>% 
  lm(fm ~ nature_time * macarthur_us_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = fm, color = high_macarthur_us_rung)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Flourishing  (fm)", color = "High Macarthur US status") 
```

## * Nature time x Macarthur US rung -> Satisfaction with life  
```{r, message=F}

df_proc %>%
  lm(swl ~ nature_time * macarthur_us_rung, .) %>%
  summary
df_proc %>%
  ggplot(aes(x = nature_time, y = swl, color = high_macarthur_us_rung)) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Satisfaction with life (swl)", color = "High Macarthur US status")
```

## Nature time x Macarthur US rung -> Negative affect   
```{r, message=F}
df_proc %>% 
  lm(panas_neg ~ nature_time * macarthur_us_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = panas_neg, color = high_macarthur_us_rung)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Negative affect (PANAS-neg)", color = "High Macarthur US status") 
```

## Nature time x Macarthur US rung -> Perceived stress 
```{r, message=F}
df_proc %>% 
  lm(pss ~ nature_time * macarthur_us_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = pss, color = high_macarthur_us_rung)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Perceived stress (pss)", color = "High Macarthur US status") 
```

## Nature time x Macarthur Community rung -> Positive affect
```{r, message=F}
df_proc %>% 
  lm(panas_pos ~ nature_time * macarthur_comm_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = panas_pos, color = high_macarthur_comm_rung)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Positive affect (PANAS-pos)", color = "High Macarthur Community status") 
```

## Nature time x Macarthur Community rung -> Flourishing 
```{r, message=F}
df_proc %>% 
  lm(fm ~ nature_time * macarthur_comm_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = fm, color = high_macarthur_comm_rung)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Flourishing (fm)", color = "High Macarthur Community status") 
```

## Nature time x Macarthur Community rung -> Satisfaction with life  
```{r, message=F}

df_proc %>%
  lm(swl ~ nature_time * macarthur_comm_rung, .) %>%
  summary
df_proc %>%
  ggplot(aes(x = nature_time, y = swl, color = high_macarthur_comm_rung)) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Satisfaction with life (swl)", color = "High Macarthur Community status")
```

## Nature time x Macarthur Community rung -> Negative affect   
```{r, message=F}
df_proc %>% 
  lm(panas_neg ~ nature_time * macarthur_comm_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = panas_neg, color = high_macarthur_comm_rung)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Negative affect (PANAS-neg)", color = "High Macarthur Community status") 
```

## Nature time x Macarthur Community rung -> Perceived stress 
```{r, message=F}
df_proc %>% 
  lm(pss ~ nature_time * macarthur_comm_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = pss, color = high_macarthur_comm_rung)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Perceived stress (pss)", color = "High Macarthur Community status") 
```



# 2b: Moderations mediated by reappraisal and rumination 
We hypothesize that these moderations will be mediated by frequency of reappraisal and rumination.

## Nature time x ACE binary -> Reappraisal -> Pos affect 
* Non-significant indirect effect 
```{r, message=F}
mod <- '
pmerq_reappraise ~ a*nature_time:high_ace + nature_time + high_ace
panas_pos ~ b*pmerq_reappraise + cp*nature_time:high_ace + nature_time + high_ace
indirect := a*b
total := indirect + cp
'
fit <- df_proc %>% 
  sem(mod,
      se="bootstrap",
      data=.)
summary(
  fit,
  fit.measures=T,
  rsq=T,
  standardized=T
)

parameterEstimates(
  fit,
  boot.ci.type="bca.simple",
  level=0.95,
  ci=TRUE,
  standardized = TRUE
) %>%
  as.data.frame %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  select(-std.lv, -std.nox)
```

## Nature time x ACE -> Rumination -> Pos affect 
* Non-significant indirect effect
```{r, message=F}
mod <- '
rrs_brood ~ a*nature_time:high_ace + nature_time + high_ace
panas_pos ~ b*rrs_brood + cp*nature_time:high_ace + nature_time + high_ace
indirect := a*b
total := indirect + cp
'
fit <- df_proc %>% 
  sem(mod,
      se="bootstrap",
      data=.)
summary(
  fit,
  fit.measures=T,
  rsq=T,
  standardized=T
)

parameterEstimates(
  fit,
  boot.ci.type="bca.simple",
  level=0.95,
  ci=TRUE,
  standardized = TRUE
) %>%
  as.data.frame %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  select(-std.lv, -std.nox)
```

## Nature time x ACE -> Reappraisal -> Neg affect 
* Non-significant indirect effect
```{r, message=F}
mod <- '
pmerq_reappraise ~ a*nature_time:high_ace + nature_time + high_ace
panas_neg ~ b*pmerq_reappraise + cp*nature_time:high_ace + nature_time + high_ace
indirect := a*b
total := indirect + cp
'
fit <- df_proc %>% 
  sem(mod,
      se="bootstrap",
      data=.)
summary(
  fit,
  fit.measures=T,
  rsq=T,
  standardized=T
)

parameterEstimates(
  fit,
  boot.ci.type="bca.simple",
  level=0.95,
  ci=TRUE,
  standardized = TRUE
) %>%
  as.data.frame %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  select(-std.lv, -std.nox)
```

## Nature time x ACE -> Rumination -> Neg affect
* Non-significant indirect effect
```{r, message=F}
mod <- '
rrs_brood ~ a*nature_time:high_ace + nature_time + high_ace
panas_neg ~ b*rrs_brood + cp*nature_time:high_ace + nature_time + high_ace
indirect := a*b
total := indirect + cp
'
fit <- df_proc %>% 
  sem(mod,
      se="bootstrap",
      data=.)
summary(
  fit,
  fit.measures=T,
  rsq=T,
  standardized=T
)

parameterEstimates(
  fit,
  boot.ci.type="bca.simple",
  level=0.95,
  ci=TRUE,
  standardized = TRUE
) %>%
  as.data.frame %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  select(-std.lv, -std.nox)
```

## Nature time x Macarthur US -> Reappraisal -> SWL
* Non-significant indirect effect 
```{r, message=F}
mod <- '
pmerq_reappraise ~ a*nature_time:macarthur_us_rung + nature_time + macarthur_us_rung
swl ~ b*pmerq_reappraise + cp*nature_time:macarthur_us_rung + nature_time + macarthur_us_rung
indirect := a*b
total := indirect + cp
'
fit <- df_proc %>% 
  sem(mod,
      se="bootstrap",
      data=.)
summary(
  fit,
  fit.measures=T,
  rsq=T,
  standardized=T
)

parameterEstimates(
  fit,
  boot.ci.type="bca.simple",
  level=0.95,
  ci=TRUE,
  standardized = TRUE
) %>%
  as.data.frame %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  select(-std.lv, -std.nox)
```

## Nature time x Macarthur US -> Rumination -> SWL
* Non-significant indirect effect 
```{r, message=F}
mod <- '
rrs_brood ~ a*nature_time:macarthur_us_rung + nature_time + macarthur_us_rung
swl ~ b*rrs_brood + cp*nature_time:macarthur_us_rung + nature_time + macarthur_us_rung
indirect := a*b
total := indirect + cp
'
fit <- df_proc %>% 
  sem(mod,
      se="bootstrap",
      data=.)
summary(
  fit,
  fit.measures=T,
  rsq=T,
  standardized=T
)

parameterEstimates(
  fit,
  boot.ci.type="bca.simple",
  level=0.95,
  ci=TRUE,
  standardized = TRUE
) %>%
  as.data.frame %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  select(-std.lv, -std.nox)
```

# Session Info
```{r, message=F}
sessionInfo()
```

