---
title: "Nature ER National Qualtrics Study"
author: "Ashish"
date: "4/26/2021"
output: rmdformats::readthedown
---

# Notes
## TODO (for Ashish)
* Need to figure out how to deal with heteroscedasticity for time in nature. E.g. in mediation models
  * Lim & Melville. (2009). Robustness of Structural Equation Modeling to Distributional Misspecification: Empirical Evidence & Research Guidelines 
* Mediated moderation

# Initialization
```{r, message=FALSE}
rm(list=ls())
library(lavaan)
library(lmerTest)

library(here)
library(tidyverse)
library(tidylog)
require(rmdformats)
theme_set(theme_bw())
```

# Preprocessing 
## Functions 
```{r}
codebook_renamer <- function(df, codebook, old_col_name="old_col_name", new_col_name="new_col_name"){
  codebook <- codebook %>%
    dplyr::filter(.data[[old_col_name]] %in% names(df))
  df %>% 
  rename_at(vars(codebook[[old_col_name]]), ~codebook[[new_col_name]])
}
recoder <- function(column, var_regex, var_col_name, codebook=codebook_values){
  codebook <- codebook %>%
    dplyr::filter(!is.na(old_value) | !is.na(new_value)) %>% 
    dplyr::mutate_at(vars(old_value, new_value), ~replace_na(., "<na_value>"))
  column <- column %>% 
    replace_na(., "<na_value>")
	level_key <- codebook %>%
	  dplyr::filter(.data[[var_col_name]]==!!var_regex) %>% 
	  dplyr::mutate(old_value = tolower(old_value)) %>% 
		dplyr::select(old_value, new_value) %>%
		deframe
	level_key <- c(level_key, "<na_value>"=NA)
	recoded_column <- recode(tolower(column), !!!level_key)
	recoded_column <- as.numeric(recoded_column)
	 return(recoded_column)
}
codebook_recoder <- function(df, codebook, var_col_name="var_regex"){
  var_regexes <- unique(codebook[[var_col_name]])
  for(var in var_regexes){
    df <- df %>% 
      dplyr::mutate_at(vars(matches(paste0("^", var))), 
                       ~recoder(., var_regex=var, var_col_name=var_col_name))
  }
  return(df)
}
tally_scale <- function(df, 
                        scale_regex, 
                        new_col_name=NULL, 
                        pid_col="pid", 
                        join_function=dplyr::full_join, 
                        na.rm=F, 
                        tally_function=sum){
  # if user did not supply a new column name, use the scale_regex
  if(is.null(new_col_name)) new_col_name <- scale_regex 
  # check is there are duplicate participant IDs
  if(any(duplicated(df[[pid_col]]))){stop("Duplicate IDs found")}
  # append caret to start of regex
  scale_regex <- paste0("^", scale_regex) 
  # identify columns to tally
  cols_to_tally <- names(df)[str_detect(names(df), scale_regex)] 
  print(paste0("[",new_col_name, "] tallying columns:"))
  print(cols_to_tally)
  df_tally <- df %>% 
    dplyr::select(one_of(pid_col), one_of(cols_to_tally)) %>% # select columns to aggregate
    tidyr::pivot_longer(-one_of(pid_col)) %>% # convert to long format 
    dplyr::group_by_at(pid_col) %>% # group by participant
    dplyr::mutate(value = as.numeric(value)) %>% # change values to numeric
    dplyr::summarize(!!new_col_name := tally_function(value, na.rm=na.rm)) # aggregate according to tally_function
  if(!is.null(join_function)){
    df_tally <- df %>%
      join_function(df_tally) # join aggregated scores with original dataframe using join_function
  }
  return(df_tally)
}

```

## Read data
```{r}
codebook_filepath <- here("lib/Winter_2020_Survey_EWB_S2B_National_April_26_2021_11_30_codebook.xlsx")
codebook_vars <- readxl::read_excel(codebook_filepath, sheet="variables")
codebook_values <- readxl::read_excel(codebook_filepath, sheet="values") %>% 
  mutate(old_value = str_replace_all(old_value, "\r", ""))

df_file <- read_csv(here("data/raw/Winter 2020 Survey EWB - S2B (National)_April 29, 2021_16.30.csv"))
df_raw <- df_file %>% 
  slice(-1:-2) %>% 
  # -- rename columns -- #
  codebook_renamer(codebook=codebook_vars)


```

## Constants
```{r}
columns_to_numeric <- c("nature_time", "age")
```


## Process data
TODO: 
* The tally_scale() function takes
```{r}
df_recoded <- df_raw %>%
	# -- recode variables -- #
	codebook_recoder(codebook=codebook_values)

df_proc <- df_recoded %>%
  
  # -- remove failed attention checks -- #
  filter(ac_1 == 1 & ac_2 == 1 & ac_3 == 1 & ac_4 == 1) %>% 
  
  # -- remove incompletes -- #
  filter(Progress == "100") %>% 
  
  # -- remove people who took survey twice -- #
  filter(!(pid %in% .$pid[duplicated(pid)])) %>% 

  # -- tally scales -- # 
  tally_scale("paq.*[0-9]{1,2}$", "paq") %>% 
  tally_scale("paq_.*_dif_[0-9]{1,2}$", "paq_dif") %>% 
  tally_scale("paq_.*_ddf_[0-9]{1,2}$", "paq_ddf") %>% 
  tally_scale("paq_.*_eot_[0-9]{1,2}$", "paq_eot") %>% 
  tally_scale("paq_pos_.*_[0-9]{1,2}$", "paq_pos") %>% 
  tally_scale("paq_neg_.*_[0-9]{1,2}$", "paq_neg") %>% 
  tally_scale("paq_neg_dif_[0-9]{1,2}$", "paq_neg_dif") %>% 
  tally_scale("paq_neg_ddf_[0-9]{1,2}$", "paq_neg_ddf") %>% 
  tally_scale("paq_pos_dif_[0-9]{1,2}$", "paq_pos_dif") %>% 
  tally_scale("paq_pos_ddf_[0-9]{1,2}$", "paq_pos_ddf") %>% 
  
  tally_scale("pmerq_(recons|repurp)_.*_[0-9]{1,2}$", "pmerq_reappraise") %>% 
  tally_scale("pmerq_attdep_.*_[0-9]{1,2}$", "pmerq_attdep") %>% 
  
  tally_scale("sitselect_(approach|avoid)_[1-6]$", "sitselect") %>% 
  tally_scale("sitselect_approach_[1-6]$", "sitselect_approach") %>% 
  tally_scale("sitselect_avoid_[1-6]$", "sitselect_avoid") %>% 
  
  tally_scale("panas_pos_[0-9]{1,2}$", "panas_pos") %>% 
  tally_scale("panas_neg_[0-9]{1,2}$", "panas_neg") %>% 
  
  tally_scale("rrs_brood_[0-9]$", "rrs_brood") %>% 
  
  tally_scale("ace_[0-9]$", "ace") %>% 
    
  # -- data types -- #
  mutate_at(vars(one_of(columns_to_numeric)), as.numeric) %>% 
  # -- re-order factors -- #
  mutate(edu = factor(edu, levels = c( 
    "Less than high school degree",
    "High school graduate (high school diploma or equivalent including GED)",
    "Some college but no degree",
    "Associate degree in college (2-year)",
    "Bachelor's degree in college (4-year)",
    "Master's degree",
    "Professional degree (JD, MD)",
    "Doctoral degree"
  ))) %>% 
  # -- discretizing continuous variables for visualizations -- #
  mutate(high_ace = case_when(ace <= 4 ~ "1", ace > 4 ~ "0")) %>% 
  mutate(high_macarthur_us_rung = case_when(macarthur_us_rung <= median(macarthur_us_rung) ~ "1",
                                            macarthur_us_rung > median(macarthur_us_rung) ~ "0")) %>% 
  mutate(high_macarthur_comm_rung = case_when(macarthur_comm_rung <= median(macarthur_comm_rung) ~ "1",
                                              macarthur_comm_rung > median(macarthur_comm_rung) ~ "0"))
```


```{r, echo=FALSE}
# ------ End Preprocessing ------ #
# ----- Run all chunks above -----#
```

# Preregistration 
## Hypotheses
[Pre-registration](https://osf.io/t94h2) 

1A. We hypothesize that nature contact will be associated with greater frequency of (i) situation selection in the form of approaching positively valenced situations, (ii) distraction, and (iii) reappraisal strategies and (iv) lesser frequency of rumination. Moreover, we hypothesize that emotion regulation strategies will be related to affective outcomes.

1B. We hypothesize that frequency of distraction, reappraisal, and rumination will mediate the association of nature contact with affective outcomes.

2A. We hypothesize that nature contact will moderate the associations of (i) adverse life experiences and (ii) perceived social status with affective outcomes.

2B. We hypothesize that these moderations will be mediated by frequency of reappraisal and rumination.

## Statistical analysis 

Multiple regression models will test whether time with nature predicts positive affect, negative affect, and emotion regulation (reappraisal, rumination, suppression); and whether situation selection predicts time with nature; controlling for fear of COVID-19, Nature Relatedness, and age/demographic covariates. We will use model comparison procedures (i.e. LR-test and AIC/BIC) to determine whether covariates improve model fit and include them in the final model contingent on this procedure. Multiple regression analysis will also allow for us to test whether the relationship between ACE scores and perceived social status with affect is moderated by time with nature.

Structural equation modeling will be used to test whether emotion regulation mediates the association of time with nature with affective outcomes. We will evaluate bootstrapped confidence intervals for indirect effects to determine significance of mediation.

## Data exclusion

Participants must pass 4/4 attention checks to be included.

Following Leiner (2019), we will remove participants based on implausible completion times using the following procedure: "For each page, the sample’s median page completion time is divided by the individual completion time, resulting in a speed factor. A factor of 2 means that the respondent has completed a page twice as fast as the typical respondent. An average speed factor per respondent is computed after the page factors are clipped to a maximum value of 3."
We will exclude participants who respond with an average speed factor greater than 2.

Sensitivity analyses will be run to compare results with and without outliers. 


# Initial data exploration 

## Distributions 

###  Total N
```{r}
df_proc %>% 
  nrow
df_proc %>% 
  pull(pid) %>% 
  unique %>% 
  length
```

### Demographics

#### Gender
```{r}
df_proc %>% 
  group_by(gender) %>% 
  summarize(n = n())
```

#### Age
* This is why it's so important to get to know your data. See anything odd? :)
```{r}
df_proc %>% 
  ggplot(aes(x = age)) + 
  geom_histogram() + 
  labs(x = "Age", y = "count") + 
  ggtitle("Age histogram")

# Get mean age and standard deviation
df_proc %>% 
  summarize(mean_age = mean(age, na.rm = T),
            sd_age = sd(age, na.rm = T))

```

TODO: 
* Create a histogram for each the two Macarthur social status measures
* Create a bar
#### MacArthur status
```{r}

```

#### Education
```{r}
df_proc %>% 
  ggplot(aes(x = edu)) + 
  geom_bar() +
  labs(x = "Education", y = "count") +
  coord_flip() # rotate the plot
```

#### Income
TODO: 
* Re-order the income bracket categories in the preprocessing script above (see example with education)
* Create bar plot (see example with education)
```{r}

```

#### Race
* Future TODO - (don't worry about for now)
  * break apart multi-racial lines to get counts for each race 
```{r}
df_proc %>% 
  group_by(race) %>% 
  summarize(n = n())
  
```

TODO:
* Create histograms for continuous variables
  * e.g. time in nature, perceived exertion
* Create barplots for the categorical variables, reordering the factors when needed 
  * e.g. frequency of nature contact, nature setting

### Nature 

#### Time in nature 
> Over the last month, approximately how many HOURS PER WEEK do you consider yourself to have interacted with nature? This includes, for example, walking, biking, or recreating outside in local, regional, or national parks, at the beach, beside or within lakes, creeks, or the ocean, gardening or tending to plants, camping, fishing, reading or walking outside next to trees, engaging in yard work with natural elements, etc...

* Highly skewed distribution

```{r}

df_proc %>% 
  ggplot(aes(x = nature_time)) + 
  geom_histogram() + 
  labs(x = "hours/week in nature", y = "count") + 
  ggtitle("Hours/week in nature histogram")

# df_proc %>% 
#   ggplot(aes(x = log(nature_time))) + 
#   geom_histogram() + 
#   labs(x = "log transformed hours/week in nature", y = "count") + 
#   ggtitle("Log-transformed hours/week in nature histogram")
```

#### Frequency of nature contact 
> About how often do you usually visit or pass through outdoor natural areas for any reason? This includes, for example, walking, biking, or recreating outside in local, regional, or national parks, at the beach, beside or within lakes, creeks, or the ocean, gardening or tending to plants, camping, fishing, reading or walking outside next to trees, engaging in yard work with natural elements, etc...

```{r}

```

#### Nature setting
> Which option best describes where, in the past month, most of your nature exposure took place? If you spent time in multiple nature areas, please pick the option where you spent the most time. 

```{r}

```

#### Perceived exertion in nature
> Please rate your perception of exertion, i.e. how heavy and strenuous the exercise felt to you and how tired you were, when you were in the natural area during which you spent the most time in the past month. The perception of exertion is mainly felt as strain and fatigue in your muscles and as breathlessness or aches in the chest. Use this scale from 6 to 20, where 6 means “No exertion at all” and 20
means “Maximal exertion.”

```{r}

```


TODO:
* tally scales for relevant variables in preprocessing script above
* create histograms for each variable

### Emotion regulation 

#### Situation selection frequency 
Vars: 
* sitselect 
* sitselect_approach 
* sitselect_avoid 
* pmerq_sitsel_eng 
* pmerq_sitsel_dis 
```{r}

```

#### Situation modification frequency
Vars: 
* pmerq_sitmod_eng 
* pmerq_sitmod_dis 
```{r}

```

#### Distraction frequency
Vars: 
* pmerq_attdep 
* pmerq_attdep_eng 
* pmerq_attdep_dis 
```{r}

```

#### Rumination frequency 
Vars: 
* rrs_brood 
```{r}

```

#### Reappraisal frequency 
Vars:
* pmerq_reappraise (this variable is not in the codebook, but I already made it in the preprocessing script)
* pmerq_recons 
* pmerq_recons_eng
* pmerq_recons_dis
* pmerq_repurp 
* pmerq_repurp_eng  
* pmerq_repurp_dis 
```{r}

```

#### Suppression frequency 
Vars:
* pmerq_respmod_dis 
```{r}

```

#### Social support frequency 
Vars:
* pmerq_respmod_eng  
```{r}

```


### Affective outcomes 

#### Flourishing 
Vars:
* fm
```{r}

```

#### Satisfaction with life 
Vars:
* swl 
```{r}

```

#### Positive affect (PANAS)
Vars: 
* panas_pos 
```{r}

```

#### Negative affect (PANAS) 
Vars: 
* panas_neg 
```{r}

```

#### Perceived Stress 
Vars:
* pss 
```{r}

```


### Other variables

#### Alexithymia PAQ 
Vars: 
* paq 
* paq_dif 
* paq_ddf 
* paq_eot 
* paq_pos 
* paq_neg 
```{r}

```

#### Alexithymia TAS 
Vars: 
* tas 
* tas_dif 
* tas_ddf 
* tas_eot
```{r}

```


#### Fear of coronavirus 
Vars: 
* fcv 
```{r}

```

#### Social desiribility 
Vars: 
* sds 
```{r}

```


# Confirmatory analysis

## 1a: Nature contact and ER frequency 
We hypothesize that nature contact will be associated with greater frequency of (i) situation selection in the form of approaching positively valenced situations, (ii) distraction, and (iii) reappraisal strategies and (iv) lesser frequency of rumination. Moreover, we hypothesize that emotion regulation strategies will be related to affective outcomes. 

### Nature time <-> situation selection approach pos
Results 
* Significant association
* Heteroscedasticity 
```{r}
cor.test(df_proc$nature_time, df_proc$sitselect_approach)

df_proc %>% 
  ggplot(aes(x = sitselect_approach, y = nature_time)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

TODO:
* Conduct the following bivariate correlations following the template above 

### Nature time <-> distraction 
```{r}

```

### Nature time <-> reappraisal 
```{r}

```

### Nature time <-> rumination 
```{r}

```

### Nature time <-> flourishing 
```{r}

```

### Nature time <-> perceived stress 
```{r}

```

### Nature time <-> positive affect 
```{r}

```

### Nature time <-> negative affect 
```{r}

```


## 1b: Nature exposure -> ER -> affect 
We hypothesize that frequency of distraction, reappraisal, and rumination will mediate the association of nature contact with affective outcomes.

#### Nature time -> Rumination -> Negative affect
```{r}
# Step 1: Check for total effect
df_proc %>% 
  lm(rrs_brood ~ nature_time, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = rrs_brood)) +
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Brooding (RRS)")

# If Step 1 is significant, continue to Step 2...

# Step 2: Conduct mediation analysis
mod <- '
rrs_brood ~ a*nature_time
panas_neg ~ b*rrs_brood + cp*nature_time
indirect := a*b
total := indirect + cp
'
fit <- sem(mod, 
           se="bootstrap",
           data=df_proc)
summary(
  fit, 
  fit.measures=T, 
  rsq=T, 
  standardized=T
)

parameterEstimates(
  fit,
  boot.ci.type="bca.simple",
  level=0.95,
  ci=TRUE,
  standardized = TRUE
) %>% 
  as.data.frame %>% 
  mutate_if(is.numeric, ~round(., 3)) %>% 
  select(-std.lv, -std.nox)
```

TODO: 
* Conduct mediations following the template above 
  * In the first slot, you can always use nature_time
  * In the second position, you can use rrs_brood, pmerq_attdep_dis, pmerq_reappraise
  * In the third position, you can use panas_pos, panas_neg, fm, pss, swl
* (I didn't add the code chunks or headlines this time--you can add them. By running all possible combinations, we should end up with 15 code chunks.)



## 2a: Nature contact moderates association of adverse experience and affect 
We hypothesize that nature contact will moderate the associations of (i) adverse life experiences and (ii) perceived social status with affective outcomes. 


TODO: 
* Conduct moderation analyses using the templates 

#### Nature time x adverse childhood experiences -> Positive affect 
```{r}

```

#### Nature time x adverse childhood experiences -> Flourishing 
```{r}

```

#### Nature time x adverse childhood experiences -> Satisfaction with life  
```{r}

```

#### Nature time x adverse childhood experiences -> Negative affect 
```{r}
df_proc %>% 
  lm(panas_neg ~ nature_time * ace, .) %>% 
  summary
df_proc %>% 
  lm(panas_neg ~ nature_time * high_ace, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = panas_neg, color = high_ace)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Negative affect (PANAS-neg)", color = "High ACE") 
```


#### Nature time x adverse childhood experiences -> Perceived stress 
```{r}

```

#### Nature time x Macarthur US rung -> Positive affect
```{r}
df_proc %>% 
  lm(panas_neg ~ nature_time * macarthur_us_rung, .) %>% 
  summary
df_proc %>% 
  lm(panas_neg ~ nature_time * high_macarthur_us_rung, .) %>% 
  summary
df_proc %>% 
  ggplot(aes(x = nature_time, y = panas_neg, color = high_macarthur_us_rung)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm") +
  labs(x = "Hrs/week in nature", y = "Positive affect (PANAS-pos)", color = "High Macarthur US status") 
```

#### Nature time x Macarthur US rung -> Flourishing 
```{r}

```

#### Nature time x Macarthur US rung -> Satisfaction with life  
```{r}

```

#### Nature time x Macarthur US rung -> Negative affect   
```{r}

```

#### Nature time x Macarthur US rung -> Perceived stress 
```{r}

```

#### Nature time x Macarthur Community rung -> Positive affect
```{r}

```

#### Nature time x Macarthur Community rung -> Flourishing 
```{r}

```

#### Nature time x Macarthur Community rung -> Satisfaction with life  
```{r}

```

#### Nature time x Macarthur Community rung -> Negative affect   
```{r}

```

#### Nature time x Macarthur Community rung -> Perceived stress 
```{r}

```



## 2b: Moderations mediated by reappraisal and rumination 
We hypothesize that these moderations will be mediated by frequency of reappraisal and rumination.
**We can wait on this section for now**





# Session Info
```{r}
sessionInfo()
```

